---
title: "NBA Player Dashboard"
output: 
  flexdashboard::flex_dashboard:
    theme: flatly
    orientation: rows
    vertical_layout: fill
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(DT)

# variables set up
thisYear <- substr(Sys.Date(),1,4)
if (substr(Sys.Date(),6,7) > '08'){
  seasonOffset <- 0
} else {
  seasonOffset <- 1
}
thisSeason <- paste0(as.numeric(substr(Sys.Date(),1,4))-seasonOffset,"-",as.numeric(substr(Sys.Date(),1,4))-seasonOffset+1) 

# helper functions
files <- list.files("helper_functions", full.names = TRUE, recursive = TRUE)
for (f in files) source(f, local = TRUE)

# read data
team_stats <- read.csv("data/teamStats.csv") # from write_TeamStats.R
franchises <- read.csv("data/franchisesHistory.csv",stringsAsFactors = FALSE) 
team_stats <- merge(team_stats,franchises,by.x="Team",by.y="Franchise",all.x=TRUE)
#
playersHist <- read.csv("data/playersHist.csv", stringsAsFactors = FALSE) # from write_playersHist.R
playersHist <- .rename_PlayerDuplicates(playersHist) # differentiate players with the same name
playersPredictedStats_adjMin <- read.csv("data/playersNewPredicted_Final_adjMin.csv", stringsAsFactors = FALSE)
playersPredictedStats_adjPer <- read.csv("data/playersNewPredicted_Final_adjPer.csv", stringsAsFactors = FALSE)

# load neuralnet models
load("data/modelNeuralnet5_PTS.Rdata")
nn_Offense <- model$finalModel
load("data/modelNeuralnet5_PTSA.Rdata")
nn_Defense <- model$finalModel

# compute teams and players Offense and Defense
playersNewPredicted_Final_adjMinPer2 <- select(playersPredictedStats_adjPer, -contains("Per"), -effFG, -effFGA, -effPTS, -effTRB)
playersNewPredicted_OffDef <- mutate(playersNewPredicted_Final_adjMinPer2, Tm = Player, effMin = 1)
playersPredicted <- .teamsPredictedPower(data = playersNewPredicted_OffDef,actualOrPred="predicted") %>%
  mutate(Player = substr(team_season,1,regexpr("_",team_season)-1),plusMinus = TEAM_PTS-TEAM_PTSAG) %>%
  select(Player,Offense = TEAM_PTS, Defense = TEAM_PTSAG, plusMinus) %>%
  as.data.frame()
playersPredicted2 <- merge(playersPredicted,
                           playersPredictedStats_adjMin[,c("Player","Exp","Age","Tm","effMin")], by = "Player") %>%
  mutate(adjPlusMinus = plusMinus*effMin*100) %>%
  group_by(Tm) %>%
  mutate(teamPlusMinus = sum(adjPlusMinus,na.rm=TRUE)) %>%
  ungroup()

playerDashboard <- merge(playersPredictedStats_adjPer,select(playersPredicted2, -c(Age,Tm,effMin)), by = "Player")

playerRanks <- mutate_if(playerDashboard, is.numeric, function(x) row_number(desc(x)))

playerMax <- summarise_if(playerDashboard, is.numeric, max)
playerMin <- group_by(playerDashboard, Player) %>% summarise_if(is.numeric, min)

# tSNE for similiarity and historical evolution of players
tsne_ready_hist <- read.csv("data/tsne_ready_hist.csv", stringsAsFactors = FALSE)
# tSNE for predicted stats in new season
tsne_ready <- read.csv("data/tsne_ready_newSeason.csv", stringsAsFactors = FALSE)

############################
# Team loads
# Actual Season schedule
realSeasonSchedule <- read.csv("data/realSeasonSchedule.csv",stringsAsFactors = FALSE) # from write_seasonSchedule.R
datesRange <- unique(realSeasonSchedule$Date)
### Global hyperparameters for Normal distributions
# get game scores from past 7 seasons (since 2010)
gameScores <- read.csv("data/gameScores.csv", stringsAsFactors = FALSE) # write_scoreDifferentials.R 
#sigmaHome <- sd(as.numeric(gameScores$pts_home), na.rm = TRUE)
#sigmaAway <- sd(as.numeric(gameScores$pts_away), na.rm = TRUE)
sigma <- sd(c(as.numeric(gameScores$pts_home),as.numeric(gameScores$pts_away)), na.rm = TRUE)
avgHome <- mean(as.numeric(gameScores$pts_home), na.rm = TRUE)
avgAway <- mean(as.numeric(gameScores$pts_away), na.rm = TRUE)
global_mean <- mean(c(as.numeric(gameScores$pts_home),as.numeric(gameScores$pts_away)), na.rm = TRUE)
home_away_factor <- avgHome - avgAway # how many extra points does a team score on average when playing home
# Teams Predicted powers and wins
teamsPredicted <- .teamsPredictedPower(data = playersNewPredicted_Final_adjMinPer2,actualOrPred="predicted")
win_predictions <- .teamsPredictedWins() 

teamDashboard <- merge(teamsPredicted, win_predictions, by.x = "TeamCode", by.y = "team") %>%
  select(Tm = TeamCode, TeamOffense = TEAM_PTS, TeamDefense = TEAM_PTSAG, Season, wins)
teamRanks <- mutate_if(teamDashboard, is.numeric, function(x) row_number(desc(x)))

teamStats <- .computeTeamStats(data = playersPredictedStats_adjPer)
teamStatRanks <- mutate_if(teamStats, is.numeric, function(x) row_number(desc(x)))
teamRanks <- merge(teamStatRanks, select(teamRanks,-Season),by="Tm")
teamMax <- summarise_if(teamStats, is.numeric, max)

# t-SNE for teams
tsne_ready_teams <- read.csv("data/tsne_ready_teams.csv", stringsAsFactors = FALSE)

##########################
# Regular Season schedule
conferences <- read.csv("data/nba_conferences.csv", stringsAsFactors = FALSE) # Same as franchises 
realSeasonSchedule <- read.csv("data/realSeasonSchedule.csv",stringsAsFactors = FALSE) # from write_seasonSchedule.R
datesRange <- unique(realSeasonSchedule$Date)
regSeasonOutcome <- .standings(real=TRUE)

```

Players
=====================================

Row {.sidebar}
-----------------------------------------------------------------------

```{r}
selectizeInput("playerName", "Select Player", choices = playerDashboard$Player, selected = playerDashboard$Player[1])

```


Row
-------------------------------------------------------------------------

### Offense {.value-box}
```{r}

vOff <- reactive({
  data <- filter(playerDashboard, Player == input$playerName) %>%
    select(Offense) %>% as.numeric()
  data
})

rOff <- reactive({
  data <- filter(playerRanks, Player == input$playerName) %>%
    select(Offense) %>% as.numeric()
  data
})

renderValueBox({
  
  valueBox(
    value = formatC(vOff(), digits = 1, format = "f"),
    caption = paste0("Offense (#",rOff(),")"),
    icon = "",
    color = ifelse(rOff() < nrow(playerRanks)/3,"green",ifelse(rOff() < nrow(playerRanks)*2/3,"lightblue","red"))
  )
})
```

### Defense {.value-box}
```{r}

vDef <- reactive({
  data <- filter(playerDashboard, Player == input$playerName) %>%
    select(Defense) %>% as.numeric()
  data
})

rDef <- reactive({
  data <- filter(playerRanks, Player == input$playerName) %>%
    mutate(Defense = nrow(playerRanks)-Defense+1) %>%
    select(Defense) %>% as.numeric()
  data
})

renderValueBox({
  
  valueBox(
    value = formatC(vDef(), digits = 1, format = "f"),
    caption = paste0("Defense (#",rDef(),")"),
    icon = "",
    color = ifelse(rDef() < nrow(playerRanks)/3,"green",ifelse(rDef() < nrow(playerRanks)*2/3,"lightblue","red"))
  )
})
```

### Usage Rate {.value-box}
```{r}

vMin <- reactive({
  data <- filter(playerDashboard, Player == input$playerName) %>%
    select(effMin) %>% as.numeric()
  data
})

rMin <- reactive({
  data <- filter(playerRanks, Player == input$playerName) %>%
    select(effMin) %>% as.numeric()
  data
})

renderValueBox({
  
  valueBox(
    value = paste0(formatC(vMin()*1000, digits = 1, format = "f"),"%"),
    caption = paste0("Usage (#",rMin(),")"),
    icon = "",
    color = ifelse(rMin() < nrow(playerRanks)/3,"green",ifelse(rMin() < nrow(playerRanks)*2/3,"lightblue","red"))
  )
})
```

### Experience {.value-box}
```{r}

vExp <- reactive({
  data <- filter(playerDashboard, Player == input$playerName) %>%
    select(Exp) %>% as.character()
  data
})

renderValueBox({
  
  valueBox(
    value = vExp(),
    icon = "",
    color = "lightgrey"
  )
})
```

### Age {.value-box}
```{r}

vAge <- reactive({
  data <- filter(playerDashboard, Player == input$playerName) %>%
    select(Age) %>% as.numeric()
  data
})

renderValueBox({
  
  valueBox(
    value = vAge(),
    icon = "",
    color = "lightgrey"
  )
})
```

### Team {.value-box}
```{r}

vTm <- reactive({
  data <- filter(playerDashboard, Player == input$playerName) %>%
    select(Tm) %>% as.character()
  data
})

renderValueBox({
  
  valueBox(
    value = vTm(),
    icon = "",
    color = "lightgrey"
  )
})
```

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Player Stats
```{r}
barplotPlayerStats <- reactive({
  
  off_def <- filter(playerDashboard, Player == input$playerName) %>% 
    select(Offense, Defense)
  #data <- filter(playerDashboard, Player == "LeBron James") %>% 
  data <- filter(playerDashboard, Player == input$playerName) %>% 
    select(contains("eff"), contains("Per")) %>%
    gather(Stat, Value) 
    #mutate(Value = ifelse(grepl("Per",Stat), paste0(round(Value*100,1),"%"),
    #                     ifelse(grepl("Min",Stat), paste0(round(Value*1000,1),"%"),round(Value,2))))
  
  ranks <- filter(playerRanks, Player == input$playerName) %>% 
  #ranks <- filter(playerRanks, Player == "LeBron James") %>% 
    select(contains("eff"), contains("Per")) %>%
    gather(Stat, Value) %>%
    mutate(color = ifelse(grepl("TOV|PF",Stat),
                          ifelse(Value > nrow(playerDashboard)/3,"green",
                                 ifelse(Value > nrow(playerDashboard)*2/3,"lightblue","red")),
                          ifelse(Value < nrow(playerDashboard)/3,"green",
                                 ifelse(Value < nrow(playerDashboard)*2/3,"lightblue","red")))) %>%
    mutate(Rank = Value) %>%
    select(-Value)
  
  data <- merge(data,ranks[,c("Stat","Rank","color")],by="Stat") %>% 
    mutate(order = c(8,7,11,10,15,20,17,5,4,2,14,13,23,18,22,1,19,21,16,6,9,3,12)) %>%
    mutate(Stat = as.factor(Stat)) %>%
    arrange(order)

  maxs <- select(playerMax, contains("eff"), contains("Per")) %>%
    gather(Stat, Value) %>%
    mutate(Stat = as.factor(Stat)) %>%
    merge(data[,c("Stat","order")],by="Stat") %>%
    arrange(order)

  data$Stat = factor(data$Stat, levels = data$Stat[order(data$order, decreasing = FALSE)], ordered=TRUE, 
                     labels = c("Points","effFG%","FG%","FG_A","FG_M","FG_2P%","FG_2PM","FG_2PA","FG_3P%","FG_3PM","FG_3PA","FT%","FT_M","FT_A","AST","TRB","DRB","ORB","STL","BLK","TOV","PF","Usage"))
  
  maxs$Stat = factor(maxs$Stat, levels = maxs$Stat[order(data$order, decreasing = FALSE)], ordered=TRUE, 
                     labels = c("Points","effFG%","FG%","FG_A","FG_M","FG_2P%","FG_2PM","FG_2PA","FG_3P%","FG_3PM","FG_3PA","FT%","FT_M","FT_A","AST","TRB","DRB","ORB","STL","BLK","TOV","PF","Usage"))
  
  ggplot(NULL) +
    geom_bar(data = data, aes(Stat, Value), stat = "identity", fill=factor(data$color)) +
    geom_bar(data = maxs, aes(Stat, Value), stat = "identity", fill = "grey", alpha = 0.3) +
    #coord_flip() +
    geom_text(data = data, aes(Stat,0.95,label = ifelse(grepl("%",Stat), paste0(round(Value*100,1),"%"),
                          ifelse(grepl("Usage",Stat), paste0(round(Value*1000,1),"%"),round(Value,2))))) +
    geom_text(data = data, aes(Stat,.85,label = paste0("(",Rank,")"))) +
    theme(legend.key=element_blank(),
              legend.title=element_blank(),
              legend.text = element_blank(),
              legend.position="none",
              plot.title = element_text(size=9),
              panel.border = element_blank(),
              panel.background = element_blank(),
              axis.text.x = element_text(size = 8),
              #axis.text.y = element_blank(),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank())
  
})

renderPlot(barplotPlayerStats())

```

### Similar Players 
```{r}

similar <- reactive({
  
  similarPlayers <- .compare10_click(thisSeason,input$playerName,data=tsne_ready) %>%
  #similarPlayers <- .compare10_click(thisSeason,"Kyrie Irving",data=tsne_ready) %>%
    top_n(11,-dist) %>% tail(10) %>% 
    merge(playerDashboard[,c("Player","Offense","Defense","effMin","Age","Tm")], by="Player") %>%
    mutate(Offense = round(Offense,1), Defense = round(Defense,1),dist = round(dist,2), effMin = paste0(formatC(effMin*1000,digits=1,format="f"),"%")) %>%
    arrange(dist) %>%
    select(Player,Team = Tm, Age, Offense, Defense, `Usage Rate` = effMin,`Euclidean dist` = dist)
    
  
  similarPlayers
})

renderTable(similar())  


```


### Similar Players Last 5 Seasons {data-width=350}
```{r}

similar_hist <- reactive({
  similarPlayers_Hist <- data.frame()
  player_seasons <- filter(tsne_ready_hist, Player == input$playerName) %>%
    arrange(desc(Season)) %>% select(Season) %>% head(5)
  for (s in player_seasons$Season) {
    thisSeason <- .compare10_click(s,input$playerName,data=tsne_ready_hist) %>%
      top_n(11,-dist) %>% tail(10) %>% mutate(player_season = paste0(Player," (",Season,")")) %>% select(player_season)
    names(thisSeason) <- c(paste0("In Season: ",s))
    if (nrow(similarPlayers_Hist) > 0) similarPlayers_Hist <- cbind(similarPlayers_Hist,thisSeason) else similarPlayers_Hist <- thisSeason
  }
  similarPlayers_Hist
})

renderTable(similar_hist())  


```

Row {.tabset .tabset-fade}
---------------------------------------------------

### Player t-SNE map 
```{r}
tsne_predicted <- reactive({
  
playerCluster <- kmeans(tsne_ready[, c("x","y")], 13, nstart = 10, iter.max = 20)
  tsne_ready2 <- cbind(tsne_ready, cluster = playerCluster$cluster)
  
  tsne_points_filter <- filter(tsne_ready2, Player == input$playerName)
    #centroid <- data.frame(x=(mean(tsne_points_filter$x)),y=mean(tsne_points_filter$y))
    x_limit <- c(min(tsne_points_filter$x)-5,max(tsne_points_filter$x)+10) 
    y_limit <- c(min(tsne_points_filter$y)-5,max(tsne_points_filter$y)+10)
  
  cluster_representative <- group_by(tsne_ready2, cluster) %>% 
    mutate(x_mean = mean(x), y_mean=mean(y)) %>%
    mutate(dist = sqrt((x-x_mean)^2+(y-y_mean)^2)) %>%
    filter(dist==min(dist)) %>%
    select(cluster, Player,Season, x,y,dist) %>%
    ungroup()
  
  if (nrow(tsne_points_filter) > 0) {   
    ggplot(NULL, aes(x,y)) +  
        geom_point(data=tsne_ready2,aes(color = as.factor(cluster)),alpha = 0.5) +
        geom_point(data=tsne_points_filter,color = "red",size=4) +
      geom_text(data = cluster_representative, aes(label = paste0(Player," (",Season,")")),size=3, nudge_y = 1) +
        geom_text(data=tsne_points_filter,aes(label = paste0(Player," (",Season,")")),size=3, nudge_y = 1) +
        theme(legend.key=element_blank(),
              legend.title=element_blank(),
              legend.text = element_blank(),
              legend.position="none",
              plot.title = element_text(size=9),
              panel.border = element_blank(),
              panel.background = element_blank(),
              axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank())
  } else {
    ggplot(NULL, aes(x,y)) +  
        geom_point(data=tsne_ready2,aes(color = as.factor(cluster)),alpha = 0.5) +
      geom_text(data = cluster_representative, aes(label = paste0(Player," (",Season,")")),size=3, nudge_y = 1) +
        theme(legend.key=element_blank(),
              legend.title=element_blank(),
              legend.text = element_blank(),
              legend.position="none",
              plot.title = element_text(size=9),
              panel.border = element_blank(),
              panel.background = element_blank(),
              axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank())
  }

})

renderPlot(tsne_predicted())
```

### t-SNE timeline
```{r}

tsne_historical <- reactive({
  
  playerCluster <- kmeans(tsne_ready_hist[, c("x","y")], 13, nstart = 10, iter.max = 20)
  tsne_ready_hist2 <- cbind(tsne_ready_hist, cluster = playerCluster$cluster)
  
  tsne_points_filter <- filter(tsne_ready_hist2, Player == input$playerName)
    #centroid <- data.frame(x=(mean(tsne_points_filter$x)),y=mean(tsne_points_filter$y))
    x_limit <- c(min(tsne_points_filter$x)-5,max(tsne_points_filter$x)+10) 
    y_limit <- c(min(tsne_points_filter$y)-5,max(tsne_points_filter$y)+10)
  
  cluster_representative <- group_by(tsne_ready_hist2, cluster) %>% 
    mutate(x_mean = mean(x), y_mean=mean(y)) %>%
    mutate(dist = sqrt((x-x_mean)^2+(y-y_mean)^2)) %>%
    filter(dist==min(dist)) %>%
    select(cluster, Player,Season, x,y,dist) %>%
    ungroup()
  
  if (nrow(tsne_points_filter) > 0) {   
    ggplot(NULL, aes(x,y)) +  
        geom_point(data=tsne_ready_hist2,aes(color = as.factor(cluster)),alpha = 0.2) +
        geom_point(data=tsne_points_filter,color = "red",size=4) +
        geom_text(data = cluster_representative, aes(label = paste0(Player," (",Season,")")),size=3, nudge_y = 1) +
        geom_text(data=tsne_points_filter,aes(label = paste0(Player," (",Season,")")),size=3, nudge_y = 1) +
        theme(legend.key=element_blank(),
              legend.title=element_blank(),
              legend.text = element_blank(),
              legend.position="none",
              plot.title = element_text(size=9),
              panel.border = element_blank(),
              panel.background = element_blank(),
              axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank())
  } else {
    ggplot(NULL, aes(x,y)) +  
      geom_point(data=tsne_ready_hist2,aes(color = as.factor(cluster)),alpha = 0.2) +
      geom_text(data = cluster_representative, aes(label = paste0(Player," (",Season,")")),size=3, nudge_y = 1) +
      theme(legend.key=element_blank(),
              legend.title=element_blank(),
              legend.text = element_blank(),
              legend.position="none",
              plot.title = element_text(size=9),
              panel.border = element_blank(),
              panel.background = element_blank(),
              axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank())
  }
})

renderPlot(tsne_historical())

```

Teams
=====================================

Row {.sidebar}
-----------------------------------------------------------------------

```{r}
selectizeInput("teamCode", "Select Team", choices = teamDashboard$Tm, selected = teamDashboard$Tm[1])

```


Row
-------------------------------------------------------------------------

### Offense {.value-box}
```{r}

vtOff <- reactive({
  data <- filter(teamDashboard, Tm == input$teamCode) %>%
    select(TeamOffense) %>% as.numeric()
  data
})

rtOff <- reactive({
  data <- filter(teamRanks, Tm == input$teamCode) %>%
    select(TeamOffense) %>% as.numeric()
  data
})

renderValueBox({
  
  valueBox(
    value = formatC(vtOff(), digits = 1, format = "f"),
    caption = paste0("Offense (#",rtOff(),")"),
    icon = "",
    color = ifelse(rtOff() < nrow(teamRanks)/3,"green",ifelse(rtOff() < nrow(teamRanks)*2/3,"lightblue","red"))
  )
})
```

### Defense {.value-box}
```{r}

vtDef <- reactive({
  data <- filter(teamDashboard, Tm == input$teamCode) %>%
    select(TeamDefense) %>% as.numeric()
  data
})

rtDef <- reactive({
  data <- filter(teamRanks, Tm == input$teamCode) %>%
    mutate(TeamDefense = nrow(teamRanks)-TeamDefense+1) %>%
    select(TeamDefense) %>% as.numeric()
  data
})

renderValueBox({
  
  valueBox(
    value = formatC(vtDef(), digits = 1, format = "f"),
    caption = paste0("Defense (#",rtDef(),")"),
    icon = "",
    color = ifelse(rtDef() < nrow(teamRanks)/3,"green",ifelse(rtDef() < nrow(teamRanks)*2/3,"lightblue","red"))
  )
})
```

### Wins {.value-box}
```{r}

vtWins <- reactive({
  data <- filter(teamDashboard, Tm == input$teamCode) %>%
    select(wins) %>% as.numeric()
  data
})

rtWins <- reactive({
  data <- filter(teamRanks, Tm == input$teamCode) %>%
    #mutate(wins = nrow(teamRanks)-wins+1) %>%
    select(wins) %>% as.numeric()
  data
})

renderValueBox({
  
  valueBox(
    value = formatC(vtWins(), digits = 1, format = "f"),
    caption = paste0("Wins (#",rtWins(),")"),
    icon = "",
    color = ifelse(rtWins() < nrow(teamRanks)/3,"green",ifelse(rtWins() < nrow(teamRanks)*2/3,"lightblue","red"))
  )
})
```

### Age {.value-box}
```{r}

vtAge <- reactive({
  data <- filter(teamStats, Tm == input$teamCode) %>%
    select(Age) %>% as.numeric()
  data
})

rtAge <- reactive({
  data <- filter(teamRanks, Tm == input$teamCode) %>%
    mutate(Age = nrow(teamRanks)-Age+1) %>%
    select(Age) %>% as.numeric()
  data
})

renderValueBox({
  
  valueBox(
    value = formatC(vtAge(), digits = 1, format = "f"),
    caption = paste0("Age (#",rtAge(),")"),
    icon = "",
    color = "lightgrey"
  )
})
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Team Stats
```{r}
barplotTeamStats <- reactive({
  
  off_def <- filter(teamDashboard, Tm == input$teamCode) %>% 
    select(TeamOffense, TeamDefense)
  #data <- filter(teamStats, Tm == "CLE") %>% 
  data <- filter(teamStats, Tm == input$teamCode) %>% 
    select(contains("eff"), contains("Per")) %>%
    gather(Stat, Value) 
   
  ranks <- filter(teamRanks, Tm == input$teamCode) %>% 
  #ranks <- filter(teamRanks, Tm == "CLE") %>% 
    select(contains("eff"), contains("Per")) %>%
    gather(Stat, Value) %>%
    mutate(color = ifelse(grepl("TOV|PF",Stat),
                          ifelse(Value > nrow(teamDashboard)/3,"green",
                                 ifelse(Value > nrow(teamDashboard)*2/3,"lightblue","red")),
                          ifelse(Value < nrow(teamDashboard)/3,"green",
                                 ifelse(Value < nrow(teamDashboard)*2/3,"lightblue","red")))) %>%
    mutate(Rank = Value) %>%
    select(-Value)
  
  data <- merge(data,ranks[,c("Stat","Rank","color")],by="Stat") %>% 
    mutate(order = c(8,7,11,10,15,20,17,5,4,2,14,13,18,22,1,19,21,16,6,9,3,12)) %>%
    mutate(Stat = as.factor(Stat)) %>%
    arrange(order)

  maxs <- select(teamMax, contains("eff"), contains("Per")) %>%
    gather(Stat, Value) %>%
    mutate(Stat = as.factor(Stat)) %>%
    merge(data[,c("Stat","order")],by="Stat") %>%
    arrange(order)

  data$Stat = factor(data$Stat, levels = data$Stat[order(data$order, decreasing = FALSE)], ordered=TRUE, 
                     labels = c("Points","effFG%","FG%","FG_A","FG_M","FG_2P%","FG_2PM","FG_2PA","FG_3P%","FG_3PM","FG_3PA","FT%","FT_M","FT_A","AST","TRB","DRB","ORB","STL","BLK","TOV","PF"))
  
  maxs$Stat = factor(maxs$Stat, levels = maxs$Stat[order(data$order, decreasing = FALSE)], ordered=TRUE, 
                     labels = c("Points","effFG%","FG%","FG_A","FG_M","FG_2P%","FG_2PM","FG_2PA","FG_3P%","FG_3PM","FG_3PA","FT%","FT_M","FT_A","AST","TRB","DRB","ORB","STL","BLK","TOV","PF"))
  
  ggplot(NULL) +
    geom_bar(data = data, aes(Stat, Value), stat = "identity", fill=factor(data$color)) +
    geom_bar(data = maxs, aes(Stat, Value), stat = "identity", fill = "grey", alpha = 0.3) +
    #coord_flip() +
    geom_text(data = data, aes(Stat,0.95,label = ifelse(grepl("%",Stat), paste0(round(Value*100,1),"%"),
                          ifelse(grepl("Usage",Stat), paste0(round(Value*1000,1),"%"),round(Value,2))))) +
    geom_text(data = data, aes(Stat,.85,label = paste0("(",Rank,")"))) +
    theme(legend.key=element_blank(),
              legend.title=element_blank(),
              legend.text = element_blank(),
              legend.position="none",
              plot.title = element_text(size=9),
              panel.border = element_blank(),
              panel.background = element_blank(),
              axis.text.x = element_text(size = 8),
              #axis.text.y = element_blank(),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank())
  
})

renderPlot(barplotTeamStats())

```

### Similar Teams 
```{r}

similarTeams <- reactive({
  
    distCouPerX <- filter(tsne_ready_teams,Tm == input$teamCode)$x
    #distCouPerX <- filter(tsne_ready_teams,Tm == "CLE")$x
    #distCouPerY <- filter(tsne_ready_teams,Tm == "CLE")$y
    distCouPerY <- filter(tsne_ready_teams,Tm == input$teamCode)$y
    
    similar_teams <- tsne_ready_teams %>%
      select(Season,Tm,x,y) %>%
      mutate(dist = sqrt((x-distCouPerX)^2+(y-distCouPerY)^2)) %>%
      arrange(dist) %>%
      select(-x,-y) %>%
      top_n(30,-dist) %>% 
      tail(29) %>% 
      merge(teamDashboard[,c("Tm","TeamOffense","TeamDefense","wins")], by="Tm") %>%
      mutate(Offense = round(TeamOffense,1), Defense = round(TeamDefense,1),dist = round(dist,2)) %>%
      arrange(dist) %>%
      select(Team = Tm, Offense, Defense, `Euclidean dist` = dist)
    
  similar_teams
})

renderTable(similarTeams())  


```

### Roster
```{r}

roster <- reactive({
  
  roster <- filter(playerDashboard, Tm == input$teamCode) %>%
    arrange(desc(effMin)) %>%
    mutate(Usage = paste0(round(effMin*1000,1),"%")) %>%
    select(Player,Pos,Age,Exp,Offense,Defense,Usage)
    
  roster
})

renderTable(roster())  

```

### Team t-SNE map 
```{r}
tsne_teamPredicted <- reactive({
  
playerCluster <- kmeans(tsne_ready[, c("x","y")], 13, nstart = 10, iter.max = 20)
  tsne_ready2 <- cbind(tsne_ready, cluster = playerCluster$cluster) %>%
    merge(playerDashboard[,c("Player","effMin","Offense","Defense")], by="Player")
  
  tsne_points_filter <- filter(tsne_ready2, Tm == input$teamCode)
    #centroid <- data.frame(x=(mean(tsne_points_filter$x)),y=mean(tsne_points_filter$y))
    #x_limit <- c(min(tsne_points_filter$x)-5,max(tsne_points_filter$x)+10) 
    #y_limit <- c(min(tsne_points_filter$y)-5,max(tsne_points_filter$y)+10)
  
  cluster_representative <- group_by(tsne_ready2, cluster) %>% 
    mutate(x_mean = mean(x), y_mean=mean(y)) %>%
    mutate(dist = sqrt((x-x_mean)^2+(y-y_mean)^2)) %>%
    filter(dist==min(dist)) %>%
    select(cluster, Player,Season, x,y,dist) %>%
    ungroup()
  
  if (nrow(tsne_points_filter) > 0) {   
    ggplot(NULL, aes(x,y)) +  
        geom_point(data=tsne_ready2,aes(color = as.factor(cluster)),alpha = 0.5) +
        geom_point(data=tsne_points_filter,color = "red",aes(size=effMin*10)) +
      geom_text(data = cluster_representative, aes(label = paste0(Player," (",Season,")")),size=3, nudge_y = 1) +
        geom_text(data=tsne_points_filter,aes(label = paste0(Player," (",Season,")")),size=3, nudge_y = 1) +
        theme(legend.key=element_blank(),
              legend.title=element_blank(),
              legend.text = element_blank(),
              legend.position="none",
              plot.title = element_text(size=9),
              panel.border = element_blank(),
              panel.background = element_blank(),
              axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank())
  } else {
    ggplot(NULL, aes(x,y)) +  
        geom_point(data=tsne_ready2,aes(color = as.factor(cluster)),alpha = 0.5) +
      geom_text(data = cluster_representative, aes(label = paste0(Player," (",Season,")")),size=3, nudge_y = 1) +
        theme(legend.key=element_blank(),
              legend.title=element_blank(),
              legend.text = element_blank(),
              legend.position="none",
              plot.title = element_text(size=9),
              panel.border = element_blank(),
              panel.background = element_blank(),
              axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank())
  }

})

renderPlot(tsne_teamPredicted())
```

### Facet t-SNE maps 
```{r}
tsne_teamPredicted_facets <- reactive({
  
  playerCluster <- kmeans(tsne_ready[, c("x","y")], 13, nstart = 10, iter.max = 20)
  tsne_ready2 <- cbind(tsne_ready, cluster = playerCluster$cluster) %>%
    merge(playerDashboard[,c("Player","Tm","effMin","Offense","Defense")], by=c("Player","Tm"))
  
    ggplot(data=tsne_ready2, aes(x,y)) +  
      #geom_point(data=tsne_ready2,aes(color = as.factor(cluster)),alpha = 0.2) +
      geom_point(data=tsne_ready2,color = "red",aes(size=effMin)) +
      #geom_text(data=tsne_ready2,aes(label = paste0(Player," (",Season,")")),size=3, nudge_y = 1) +
      theme(legend.position = "right") +
      facet_wrap(~Tm) +
       theme( plot.title = element_text(size=9),
              panel.border = element_blank(),
              panel.background = element_blank(),
              axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank())
  

})

renderPlot(tsne_teamPredicted_facets())
```


Season
=====================================

Row {.sidebar}
-----------------------------------------------------------------------

```{r}
selectizeInput('regSeasonDay', 'Select a day:', choices=datesRange, selected = datesRange[1])

```

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Game Probabilities
```{r}
games_probs <- reactive({
  predGames <- .getGameProbability("W",input$regSeasonDay)
  predGames
})
  
# reg season games
renderTable(games_probs())
```

### Standings
```{r}

standingsW_table <- reactive({
  stands <- .getConferenceStandings("W",input$regSeasonDay)
  stands
})
  
renderTable(standingsW_table())

### Standings East
standingsE_table <- reactive({
  stands <- .getConferenceStandings("E",input$regSeasonDay)
  stands
})
  
renderTable(standingsE_table())

```

### Probability Matrix
```{r}
win_probs <- reactive({
  stands <- .winProbability_matrix()
  stands
})
  
renderTable(win_probs())                        

```

Model
======================================

Row {.sidebar}
-----------------------------------------------------------------------

```{r}
selectizeInput("nnet", "Select Neural Net", choices = c("Offense","Defense"), selected = "Offense")

```

Row
----------------------------------------

### Neural Network
```{r, fig.height=6,fig.width=6}

selectNNet <- reactive({
  filename <- normalizePath(file.path('./images/',
                              paste('nnet_', input$nnet, '.png', sep='')))
  # Return a list containing the filename
    list(src = filename,
         width = '100%',
         height = '100%')
})

renderImage({
    selectNNet()
  }, deleteFile = FALSE)

```

### Model 
```{r}

thisModel <- reactive({
  if (input$nnet == "Offense") load("data/modelNeuralnet5_PTS.Rdata") else load("data/modelNeuralnet5_PTSA.Rdata")
  datatable(model$results,options = list(dom='t',pageLength = nrow(model$results), autoWidth = TRUE)) %>%
  formatStyle(c(0), target = 'row', fontSize = '80%')
})

renderDataTable(thisModel())

```

Row
----------------------------------

### Fit  
```{r}
fitPlot <- reactive({
  if (input$nnet == "Offense") {
    resp <- nn_Offense
    load("data/modelNeuralnet5_PTS.Rdata")
  } else {
     resp <- nn_Defense
     load("data/modelNeuralnet5_PTSA.Rdata")
  }
  plot(model$trainingData$.outcome,resp$response)
})

renderPlot(fitPlot())

```

### Probability Distribution

$\Large{X \sim \mathrm{N}(\hat{\mu}_O,\hat{\sigma})}$

