---
title: "NBA Player Dashboard"
resource_files:
- helper_functions/regular_season.R
- helper_functions/teams_power.R
- helper_functions/teams_tSNE.R
- helper_functions/compute_distance_teams.R
- helper_functions/changes_in_roster.R
- helper_functions/players_tSNE.R
- helper_functions/server_helper_functions.R
- helper_functions/compute_PredictedLeftovers.R
- helper_functions/neural_network.R
- helper_functions/plot_tSNE_All.R
- helper_functions/prepare_rosters.R
- helper_functions/simulate_n_seasons.R
- helper_functions/playoffs.R
- helper_functions/rename_PlayerName_Duplicates.R
- helper_functions/similarityFunctionsRookies.R
- helper_functions/season_schedule.R
- images/nnet_Defense.png
- images/nnet_Offense.png
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: flatly
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(DT)
library(shinyBS)
library(shinyjs)

# variables set up
thisYear <- substr(Sys.Date(),1,4)
if (substr(Sys.Date(),6,7) > '08'){
  seasonOffset <- 0
} else {
  seasonOffset <- 1
}
thisSeason <- paste0(as.numeric(substr(Sys.Date(),1,4))-seasonOffset,"-",as.numeric(substr(Sys.Date(),1,4))-seasonOffset+1) 

# helper functions
files <- list.files("helper_functions", full.names = TRUE, recursive = TRUE)
for (f in files) source(f, local = TRUE)

# read data
team_stats <- read.csv("data/teamStats.csv") # from write_TeamStats.R
franchises <- read.csv("data/franchisesHistory.csv",stringsAsFactors = FALSE) 
team_stats <- merge(team_stats,franchises,by.x="Team",by.y="Franchise",all.x=TRUE)
#
playersHist <- read.csv("data/playersHist.csv", stringsAsFactors = FALSE) # from write_playersHist.R
playersHist <- .rename_PlayerDuplicates(playersHist) # differentiate players with the same name
  
playersPredictedStats_adjMin <- read.csv("data/playersNewPredicted_Final_adjMin.csv", stringsAsFactors = FALSE)
playersPredictedStats_adjPer <- read.csv("data/playersNewPredicted_Final_adjPer.csv", stringsAsFactors = FALSE)

# load neuralnet models
load("data/modelNeuralnet5_PTS.Rdata")
nn_Offense <- model$finalModel
load("data/modelNeuralnet5_PTSA.Rdata")
nn_Defense <- model$finalModel
# load limits for scaled data. Each trade will trigger a predict() from the selected NNet model
# But scale limits must be kept as originally trained in the model for consistency
team_stats_Off <- .prepareModel("PTS")
team_stats_Def <- .prepareModel("PTSA")
scaleMaxMin_Off <- .getScaleLimits("PTS", team_stats_Off)
scaleMaxMin_Def <- .getScaleLimits("PTSA", team_stats_Def)
scaleMaxMin_Off <- scaleMaxMin_Off[!(row.names(scaleMaxMin_Off) %in%       
      c("FGPer","FG3Per","FG2Per","effFGPer","FTPer","effFG","effFGA","effTRB","effPTS")),]
scaleMaxMin_Def <- scaleMaxMin_Def[!(row.names(scaleMaxMin_Def) %in%       
      c("FGPer","FG3Per","FG2Per","effFGPer","FTPer","effFG","effFGA","effTRB","effPTS")),]
maxs_Off <- scaleMaxMin_Off$maxs
mins_Off <- scaleMaxMin_Off$mins
maxs_Def <- scaleMaxMin_Def$maxs
mins_Def <- scaleMaxMin_Def$mins
maxs_vector_input <- cbind(maxs_Off,maxs_Def)
mins_vector_input <- cbind(mins_Off,mins_Def)

# compute teams and players Offense and Defense
source("code_chunks/source_computeOffenseDefense.R",local=TRUE)
playersPredicted2 <- merge(playersPredicted,playersPredictedStats_adjMin[,c("Player","Exp","Age","Tm","effMin")], by = "Player") %>%
  mutate(adjPlusMinus = plusMinus*effMin*100) %>%
  group_by(Tm) %>%
  mutate(teamPlusMinus = sum(adjPlusMinus,na.rm=TRUE)) %>%
  ungroup()

playerDashboard <- merge(playersPredictedStats_adjPer,select(playersPredicted2, -c(Age,Tm,effMin)), by = "Player")
playerRanks <- mutate_if(playerDashboard, is.numeric, function(x) row_number(desc(x)))

playerMax <- summarise_if(playerDashboard, is.numeric, max)
playerMin <- summarise_if(playerDashboard, is.numeric, min)

# tSNE for similiarity and historical evolution of players
tsne_ready_hist <- read.csv("data/tsne_ready_hist.csv", stringsAsFactors = FALSE)
# tSNE for predicted stats in new season
tsne_ready <- read.csv("data/tsne_ready_newSeason.csv", stringsAsFactors = FALSE)
# intialize lists historical t-SNE
teams_list <- sort(unique(tsne_ready_hist$Tm))
ages_list <- sort(unique(tsne_ready_hist$Age))
seasons_list <- sort(unique(tsne_ready_hist$Season))
players_list <- sort(unique(tsne_ready_hist$Player))
skills_list <- names(tsne_ready_hist)[6:(ncol(tsne_ready_hist)-2)]

# Average player
avg_Exp <- mean(as.numeric(gsub("R","0",playersPredictedStats_adjMin$Exp)), na.rm=TRUE)
averagePlayer <- .calculate_AvgPlayer(playersPredictedStats_adjMin) %>% mutate(Exp = as.character(floor(avg_Exp))) %>%
  select(Player, Pos, Season, Age, Tm, Exp, everything()) %>%
  mutate(Age = round(Age,0)) %>%
  as.data.frame()
############################
# Team loads
# Actual Season schedule
realSeasonSchedule <- read.csv("data/realSeasonSchedule.csv",stringsAsFactors = FALSE) # from write_seasonSchedule.R
datesRange <- unique(realSeasonSchedule$Date)
### Global hyperparameters for Normal distributions
# get game scores from past 7 seasons (since 2009-2010)
gameScores <- read.csv("data/gameScores.csv", stringsAsFactors = FALSE) # write_scoreDifferentials.R 
#sigmaHome <- sd(as.numeric(gameScores$pts_home), na.rm = TRUE)
#sigmaAway <- sd(as.numeric(gameScores$pts_away), na.rm = TRUE)
sigma <- sd(c(as.numeric(gameScores$pts_home),as.numeric(gameScores$pts_away)), na.rm = TRUE)
avgHome <- mean(as.numeric(gameScores$pts_home), na.rm = TRUE)
avgAway <- mean(as.numeric(gameScores$pts_away), na.rm = TRUE)
global_mean <- mean(c(as.numeric(gameScores$pts_home),as.numeric(gameScores$pts_away)), na.rm = TRUE)
home_away_factor <- avgHome - avgAway # how many extra points does a team score on average when playing home
# Teams Predicted powers and wins
source("code_chunks/source_predictedPowersWins.R",local=TRUE)
##########################
# Regular Season schedule
conferences <- read.csv("data/nba_conferences.csv", stringsAsFactors = FALSE) # Same as franchises 
realSeasonSchedule <- read.csv("data/realSeasonSchedule.csv",stringsAsFactors = FALSE) # from write_seasonSchedule.R
datesRange <- unique(realSeasonSchedule$Date)
regSeasonOutcome <- .standings(real=TRUE)

###########################
# Reactive Values for Trade Market
values <- reactiveValues(playersAdjMin = NULL, playersDatabase = NULL, playersRanks = NULL, teamsDatabase = NULL, teamsRanks = NULL, teamsStats = NULL, teamsMax = NULL, playersTSNE = NULL, teamsTSNE = NULL, showTradeText = FALSE)
values$playersAdjMin <- playersPredictedStats_adjMin
values$playersDatabase <- playerDashboard
values$playersRanks <- playerRanks
values$teamsDatabase <- teamDashboard
values$teamsRanks <- teamRanks
values$teamsStats <- teamStats
values$teamsMax <- teamMax
values$playersTSNE <- tsne_ready
values$teamsTSNE <- tsne_ready_teams
###########################

```

Players
=====================================

Row {.sidebar}
-----------------------------------------------------------------------

```{r}
imageOutput('playerLogo',width = '80px',height='80px')
tags$style(type='text/css', ".selectize-input { font-size: 80%; line-height: 10px; width: 95%; min-height: 25px; max-height: 30px} .selectize-dropdown { font-size: 80%; line-height: 15px; }")
selectizeInput("playerName", "Select Player", choices = playerDashboard$Player, selected = playerDashboard$Player[1])
sliderInput("player_num_clusters", "Number of clusters", min = 2, max = 100, value = 10)
selectizeInput("player_tsne_color", "Color by", choices = c("K_means","Offense","Defense"), selected = "K_means")

output$playerLogo <- renderImage({
  filename <- normalizePath(file.path('./images',
                              paste(tolower(gsub(" ","-",input$playerName)), '.png', sep='')))
 
    # Return a list containing the filename and alt text
    list(src = filename,
         width = 80,
         height = 80,
         alt = paste("Player: ", input$playerName))

  }, deleteFile = FALSE)
```


Row
-------------------------------------------------------------------------

### Offense {.value-box}
```{r}

vOff <- reactive({
  data <- filter(values$playersDatabase, Player == input$playerName) %>%
    select(Offense) %>% as.numeric()
  data
})

rOff <- reactive({
  data <- filter(values$playersRanks, Player == input$playerName) %>%
    select(Offense) %>% as.numeric()
  data
})

renderValueBox({

  valueBox(
    value = formatC(vOff(), digits = 1, format = "f"),
    caption = paste0("Offense (#",rOff(),")"),
    icon = "",
    color = ifelse(rOff() < nrow(values$playersRanks)/3,"green",ifelse(rOff() < nrow(values$playersRanks)*2/3,"lightblue","red"))
  )
})
```

### Defense {.value-box}
```{r}

vDef <- reactive({
  data <- filter(values$playersDatabase, Player == input$playerName) %>%
    select(Defense) %>% as.numeric()
  data
})

rDef <- reactive({
  data <- filter(values$playersRanks, Player == input$playerName) %>%
    mutate(Defense = nrow(values$playersRanks)-Defense+1) %>%
    select(Defense) %>% as.numeric()
  data
})

renderValueBox({

  valueBox(
    value = formatC(vDef(), digits = 1, format = "f"),
    caption = paste0("Defense (#",rDef(),")"),
    icon = "",
    color = ifelse(rDef() < nrow(values$playersRanks)/3,"green",ifelse(rDef() < nrow(values$playersRanks)*2/3,"lightblue","red"))
  )
})
```

### Usage Rate {.value-box}
```{r}

vMin <- reactive({
  data <- filter(values$playersDatabase, Player == input$playerName) %>%
    select(effMin) %>% as.numeric()
  data
})

rMin <- reactive({
  data <- filter(values$playersRanks, Player == input$playerName) %>%
    select(effMin) %>% as.numeric()
  data
})

renderValueBox({

  valueBox(
    value = paste0(formatC(vMin()*1000, digits = 1, format = "f"),"%"),
    caption = paste0("Usage (#",rMin(),")"),
    icon = "",
    color = ifelse(rMin() < nrow(values$playersRanks)/3,"green",ifelse(rMin() < nrow(values$playersRanks)*2/3,"lightblue","red"))
  )
})
```

### Experience {.value-box}
```{r}

vExp <- reactive({
  data <- filter(values$playersDatabase, Player == input$playerName) %>%
    select(Exp) %>% as.character()
  data
})

renderValueBox({

  valueBox(
    value = vExp(),
    icon = "",
    color = "lightgrey"
  )
})
```

### Age {.value-box}
```{r}

vAge <- reactive({
  data <- filter(values$playersDatabase, Player == input$playerName) %>%
    select(Age) %>% as.numeric()
  data
})

renderValueBox({

  valueBox(
    value = vAge(),
    icon = "",
    color = "lightgrey"
  )
})
```

### Team {.value-box}
```{r}

vTm <- reactive({
  data <- filter(values$playersDatabase, Player == input$playerName) %>%
    select(Tm) %>% as.character()
  data
})

renderValueBox({

  valueBox(
    value = vTm(),
    icon = "",
    color = "lightgrey"
  )
})
```

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Player Stats
```{r}
barplotPlayerStats <- reactive({

  off_def <- filter(values$playersDatabase, Player == input$playerName) %>%
    select(Offense, Defense)
  #data <- filter(playerDashboard, Player == "LeBron James") %>%
  data <- filter(values$playersDatabase, Player == input$playerName) %>%
    select(contains("eff"), contains("Per")) %>%
    gather(Stat, Value)
    #mutate(Value = ifelse(grepl("Per",Stat), paste0(round(Value*100,1),"%"),
    #                     ifelse(grepl("Min",Stat), paste0(round(Value*1000,1),"%"),round(Value,2))))

  ranks <- filter(values$playersRanks, Player == input$playerName) %>%
  #ranks <- filter(playerRanks, Player == "LeBron James") %>%
    select(contains("eff"), contains("Per")) %>%
    gather(Stat, Value) %>%
    mutate(color = ifelse(grepl("TOV|PF",Stat),
                          ifelse(Value > nrow(values$playersDatabase)/3,"green",
                                 ifelse(Value > nrow(values$playersDatabase)*2/3,"lightblue","red")),
                          ifelse(Value < nrow(values$playersDatabase)/3,"green",
                                 ifelse(Value < nrow(values$playersDatabase)*2/3,"lightblue","red")))) %>%
    mutate(Rank = Value) %>%
    select(-Value)

  data <- merge(data,ranks[,c("Stat","Rank","color")],by="Stat") %>%
    mutate(order = c(8,7,11,10,15,20,17,5,4,2,14,13,23,18,22,1,19,21,16,6,9,3,12)) %>%
    mutate(Stat = as.factor(Stat)) %>%
    arrange(order)

  maxs <- select(playerMax, contains("eff"), contains("Per")) %>%
    gather(Stat, Value) %>%
    mutate(Stat = as.factor(Stat)) %>%
    merge(data[,c("Stat","order")],by="Stat") %>%
    arrange(order)

  data$Stat = factor(data$Stat, levels = data$Stat[order(data$order, decreasing = FALSE)], ordered=TRUE,
                     labels = c("Points","effFG%","FG%","FG_A","FG_M","FG_2P%","FG_2PM","FG_2PA","FG_3P%","FG_3PM","FG_3PA","FT%","FT_M","FT_A","AST","TRB","DRB","ORB","STL","BLK","TOV","PF","Usage"))

  maxs$Stat = factor(maxs$Stat, levels = maxs$Stat[order(data$order, decreasing = FALSE)], ordered=TRUE,
                     labels = c("Points","effFG%","FG%","FG_A","FG_M","FG_2P%","FG_2PM","FG_2PA","FG_3P%","FG_3PM","FG_3PA","FT%","FT_M","FT_A","AST","TRB","DRB","ORB","STL","BLK","TOV","PF","Usage"))

  ggplot(NULL) +
    geom_bar(data = data, aes(Stat, Value), stat = "identity", fill=factor(data$color)) +
    geom_bar(data = maxs, aes(Stat, Value), stat = "identity", fill = "grey", alpha = 0.3) +
    #coord_flip() +
    geom_text(data = data, aes(Stat,0.95,label = ifelse(grepl("%",Stat), paste0(round(Value*100,1),"%"),
                          ifelse(grepl("Usage",Stat), paste0(round(Value*1000,1),"%"),round(Value,2))))) +
    geom_text(data = data, aes(Stat,.85,label = paste0("(",Rank,")"))) +
    theme(legend.key=element_blank(),
              legend.title=element_blank(),
              legend.text = element_blank(),
              legend.position="none",
              plot.title = element_text(size=9),
              panel.border = element_blank(),
              panel.background = element_blank(),
              axis.text.x = element_text(size = 8),
              #axis.text.y = element_blank(),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank())

})

renderPlot(barplotPlayerStats())

```

### Similar Players
```{r}

similar <- reactive({

  similarPlayers <- .compare10_click(thisSeason,input$playerName,data=values$playersTSNE) %>%
  #similarPlayers <- .compare10_click(thisSeason,"Kyrie Irving",data=values$playersTSNE) %>%
    top_n(11,-dist) %>% tail(10) %>%
    merge(values$playersDatabase[,c("Player","Offense","Defense","effMin","Age","Tm")], by="Player") %>%
    mutate(Offense = round(Offense,1), Defense = round(Defense,1),dist = round(dist,2), effMin = paste0(formatC(effMin*1000,digits=1,format="f"),"%")) %>%
    arrange(dist) %>%
    select(Player,Team = Tm, Age, Offense, Defense, `Usage Rate` = effMin,`Euclidean dist` = dist)

  datatable(similarPlayers, extensions = 'Scroller', options = list(dom="t", scrollY = 150,scroller = TRUE,initComplete = JS("function(settings, json) {","$(this.api().table().header()).css({'background-color': '#fff', 'color': '#575859', 'font-size': '10px', 'font-weight': 'bold'});","}")
                                   #, columnDefs = list(list(visible = FALSE, targets = c((ncol(roster)-2):(ncol(roster)-1))))
                                   )) %>%
    formatStyle(0, target = 'row', fontSize = '70%', lineHeight = '70%') %>%
    formatStyle(c('Usage Rate'), textAlign = 'right')


})

renderDataTable(similar())


```


### Similar Players Last 5 Seasons {data-width=350}
```{r}

similar_hist <- reactive({
  similarPlayers_Hist <- data.frame()
  player_seasons <- filter(tsne_ready_hist, Player == input$playerName) %>%
    arrange(desc(Season)) %>% select(Season) %>% head(5)
  for (s in player_seasons$Season) {
    thisSeason <- .compare10_click(s,input$playerName,data=tsne_ready_hist) %>%
      top_n(11,-dist) %>% tail(10) %>% mutate(player_season = paste0(Player," (",Season,")")) %>% select(player_season)
    names(thisSeason) <- c(paste0("In Season: ",s))
    if (nrow(similarPlayers_Hist) > 0) similarPlayers_Hist <- cbind(similarPlayers_Hist,thisSeason) else similarPlayers_Hist <- thisSeason
  }

  datatable(similarPlayers_Hist, extensions = 'Scroller', options = list(dom="t",scrollY = 150,scroller = TRUE,initComplete = JS("function(settings, json) {","$(this.api().table().header()).css({'background-color': '#fff', 'color': '#575859', 'font-size': '10px', 'font-weight': 'bold'});","}")
                                   #, columnDefs = list(list(visible = FALSE, targets = c((ncol(roster)-2):(ncol(roster)-1))))
                                   )) %>%
    formatStyle(0, target = 'row', fontSize = '70%', lineHeight = '70%')

})

renderDataTable(similar_hist())


```

Row {.tabset .tabset-fade}
---------------------------------------------------

### Player t-SNE map
```{r}
tsne_predicted <- reactive({

  set.seed(456)
  playerCluster <- kmeans(values$playersTSNE[, c("x","y")], input$player_num_clusters, nstart = 10, iter.max = 20)
  tsne_ready2 <- cbind(values$playersTSNE, cluster = playerCluster$cluster)

  tsne_points_filter <- filter(tsne_ready2, Player == input$playerName)
    #centroid <- data.frame(x=(mean(tsne_points_filter$x)),y=mean(tsne_points_filter$y))
    x_limit <- c(min(tsne_points_filter$x)-5,max(tsne_points_filter$x)+10)
    y_limit <- c(min(tsne_points_filter$y)-5,max(tsne_points_filter$y)+10)

  cluster_representative <- group_by(tsne_ready2, cluster) %>%
    mutate(x_mean = mean(x), y_mean=mean(y)) %>%
    mutate(dist = sqrt((x-x_mean)^2+(y-y_mean)^2)) %>%
    filter(dist==min(dist)) %>%
    select(cluster, Player,Season, x,y,dist) %>%
    ungroup()

  if (nrow(tsne_points_filter) > 0) {
    ggplot(NULL, aes(x,y)) +
        geom_point(data=tsne_ready2,aes(color = as.factor(cluster)),alpha = 0.5) +
        geom_point(data=tsne_points_filter,color = "red",size=4) +
      geom_text(data = cluster_representative, aes(label = paste0(Player," (",Season,")")),color="grey",size=3, nudge_y = 1) +
        geom_text(data=tsne_points_filter,aes(label = paste0(Player," (",Season,")")),color="blue",size=3, nudge_y = 1) +
        theme(legend.key=element_blank(),
              legend.title=element_blank(),
              legend.text = element_blank(),
              legend.position="none",
              plot.title = element_text(size=9),
              panel.border = element_blank(),
              panel.background = element_blank(),
              axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank())
  } else {
    ggplot(NULL, aes(x,y)) +
        geom_point(data=tsne_ready2,aes(color = as.factor(cluster)),alpha = 0.5) +
      geom_text(data = cluster_representative, aes(label = paste0(Player," (",Season,")")),size=3, nudge_y = 1) +
        theme(legend.key=element_blank(),
              legend.title=element_blank(),
              legend.text = element_blank(),
              legend.position="none",
              plot.title = element_text(size=9),
              panel.border = element_blank(),
              panel.background = element_blank(),
              axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank())
  }

})

renderPlot(tsne_predicted())
```

### t-SNE timeline
```{r}

tsne_historical <- reactive({

  set.seed(456)
  playerCluster <- kmeans(tsne_ready_hist[, c("x","y")], input$player_num_clusters, nstart = 10, iter.max = 20)
  tsne_ready_hist2 <- cbind(tsne_ready_hist, cluster = playerCluster$cluster)

  tsne_points_filter <- filter(tsne_ready_hist2, Player == input$playerName)
    #centroid <- data.frame(x=(mean(tsne_points_filter$x)),y=mean(tsne_points_filter$y))
    x_limit <- c(min(tsne_points_filter$x)-5,max(tsne_points_filter$x)+10)
    y_limit <- c(min(tsne_points_filter$y)-5,max(tsne_points_filter$y)+10)

  cluster_representative <- group_by(tsne_ready_hist2, cluster) %>%
    mutate(x_mean = mean(x), y_mean=mean(y)) %>%
    mutate(dist = sqrt((x-x_mean)^2+(y-y_mean)^2)) %>%
    filter(dist==min(dist)) %>%
    select(cluster, Player,Season, x,y,dist) %>%
    ungroup()

  if (nrow(tsne_points_filter) > 0) {
    ggplot(NULL, aes(x,y)) +
        geom_point(data=tsne_ready_hist2,aes(color = as.factor(cluster)),alpha = 0.2) +
        geom_jitter(data=tsne_points_filter,color = "red",size=4,width = 1.5, height = 1.5) +
        geom_text(data = cluster_representative, aes(label = paste0(Player," (",Season,")")),color = "grey",size=3, nudge_y = 1) +
        geom_text(data=tsne_points_filter,aes(label = Season),color="blue",size=3, nudge_y = 1) +
        theme(legend.key=element_blank(),
              legend.title=element_blank(),
              legend.text = element_blank(),
              legend.position="none",
              plot.title = element_text(size=9),
              panel.border = element_blank(),
              panel.background = element_blank(),
              axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank())
  } else {
    ggplot(NULL, aes(x,y)) +
      geom_point(data=tsne_ready_hist2,aes(color = as.factor(cluster)),alpha = 0.2) +
      geom_text(data = cluster_representative, aes(label = paste0(Player," (",Season,")")),size=3, nudge_y = 1) +
      theme(legend.key=element_blank(),
              legend.title=element_blank(),
              legend.text = element_blank(),
              legend.position="none",
              plot.title = element_text(size=9),
              panel.border = element_blank(),
              panel.background = element_blank(),
              axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank())
  }
})

renderPlot(tsne_historical())

```

Teams
=====================================

Row {.sidebar}
-----------------------------------------------------------------------

```{r}
#renderUI(tags$img(src=paste0("https://i.cdn.turner.com/nba/nba/.element/img/4.0/global/logos/512x512/bg.white/svg/",input$teamCode,".svg"),width = '80px',height='80px'))
# renderUI(tags$img(src=paste0("Users/asanchez3/Desktop/Data Analysis/NBA/images/",input$teamCode,".svg"),width = '80px',height='80px'))
imageOutput('teamLogo',width = '80px',height='80px')
tags$style(type='text/css', "display:inline-block; .selectize-input { font-size: 80%; line-height: 10px; width: 65%; min-height: 25px; max-height: 30px} .selectize-dropdown { font-size: 80%; line-height: 15px; }")
selectizeInput("teamCode", "Select Team", choices = teamDashboard$Tm, selected = teamDashboard$Tm[1])
sliderInput("num_clusters", "Number of clusters", min = 2, max = 100, value = 10)
selectizeInput("team_tsne_color", "Color by", choices = c("K_means","Offense","Defense"), selected = "K_means")
radioButtons("bubble_size", "Balloon size proportional to usage?", c("Yes" = "yes",
                 "No" = "no"))

output$teamLogo <- renderImage({
  filename <- normalizePath(file.path('./images',
                              paste(input$teamCode, '.svg', sep='')))
 
    # Return a list containing the filename and alt text
    list(src = filename,
         width = 80,
         height = 80,
         alt = paste("Team: ", input$teamCode))

  }, deleteFile = FALSE)

```


Row
-------------------------------------------------------------------------

### Offense {.value-box}
```{r}

vtOff <- reactive({
  data <- filter(values$teamsDatabase, Tm == input$teamCode) %>%
    select(TeamOffense) %>% as.numeric()
  data
})

rtOff <- reactive({
  data <- filter(values$teamsRanks, Tm == input$teamCode) %>%
    select(TeamOffense) %>% as.numeric()
  data
})

renderValueBox({

  valueBox(
    value = formatC(vtOff(), digits = 1, format = "f"),
    caption = paste0("Offense (#",rtOff(),")"),
    icon = "",
    color = ifelse(rtOff() < nrow(values$teamsRanks)/3,"green",ifelse(rtOff() < nrow(values$teamsRanks)*2/3,"lightblue","red"))
  )
})
```

### Defense {.value-box}
```{r}

vtDef <- reactive({
  data <- filter(values$teamsDatabase, Tm == input$teamCode) %>%
    select(TeamDefense) %>% as.numeric()
  data
})

rtDef <- reactive({
  data <- filter(values$teamsRanks, Tm == input$teamCode) %>%
    mutate(TeamDefense = nrow(values$teamsRanks)-TeamDefense+1) %>%
    select(TeamDefense) %>% as.numeric()
  data
})

renderValueBox({

  valueBox(
    value = formatC(vtDef(), digits = 1, format = "f"),
    caption = paste0("Defense (#",rtDef(),")"),
    icon = "",
    color = ifelse(rtDef() < nrow(values$teamsRanks)/3,"green",ifelse(rtDef() < nrow(values$teamsRanks)*2/3,"lightblue","red"))
  )
})
```

### Wins {.value-box}
```{r}

vtWins <- reactive({
  data <- filter(values$teamsDatabase, Tm == input$teamCode) %>%
    select(wins) %>% as.numeric()
  data
})

rtWins <- reactive({
  data <- filter(values$teamsRanks, Tm == input$teamCode) %>%
    #mutate(wins = nrow(values$teamsRanks)-wins+1) %>%
    select(wins) %>% as.numeric()
  data
})

renderValueBox({

  valueBox(
    value = formatC(vtWins(), digits = 1, format = "f"),
    caption = paste0("Wins (#",rtWins(),")"),
    icon = "",
    color = ifelse(rtWins() < nrow(values$teamsRanks)/3,"green",ifelse(rtWins() < nrow(values$teamsRanks)*2/3,"lightblue","red"))
  )
})
```

### Age {.value-box}
```{r}

vtAge <- reactive({
  data <- filter(values$teamsStats, Tm == input$teamCode) %>%
    select(Age) %>% as.numeric()
  data
})

rtAge <- reactive({
  data <- filter(values$teamsRanks, Tm == input$teamCode) %>%
    mutate(Age = nrow(values$teamsRanks)-Age+1) %>%
    select(Age) %>% as.numeric()
  data
})

renderValueBox({

  valueBox(
    value = formatC(vtAge(), digits = 1, format = "f"),
    caption = paste0("Age (#",rtAge(),")"),
    icon = "",
    color = "lightgrey"
  )
})
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Team Stats
```{r}
barplotTeamStats <- reactive({

  off_def <- filter(values$teamsDatabase, Tm == input$teamCode) %>%
    select(TeamOffense, TeamDefense)
  #data <- filter(teamStats, Tm == "CLE") %>%
  data <- filter(values$teamsStats, Tm == input$teamCode) %>%
    select(contains("eff"), contains("Per")) %>%
    gather(Stat, Value)

  ranks <- filter(values$teamsRanks, Tm == input$teamCode) %>%
  #ranks <- filter(values$teamsRanks, Tm == "CLE") %>%
    select(contains("eff"), contains("Per")) %>%
    gather(Stat, Value) %>%
    mutate(color = ifelse(grepl("TOV|PF",Stat),
                          ifelse(Value > nrow(values$teamsDatabase)/3,"green",
                                 ifelse(Value > nrow(values$teamsDatabase)*2/3,"lightblue","red")),
                          ifelse(Value < nrow(values$teamsDatabase)/3,"green",
                                 ifelse(Value < nrow(values$teamsDatabase)*2/3,"lightblue","red")))) %>%
    mutate(Rank = Value) %>%
    select(-Value)

  data <- merge(data,ranks[,c("Stat","Rank","color")],by="Stat") %>%
    mutate(order = c(8,7,11,10,15,20,17,5,4,2,14,13,18,22,1,19,21,16,6,9,3,12)) %>%
    mutate(Stat = as.factor(Stat)) %>%
    arrange(order)

  maxs <- select(values$teamsMax, contains("eff"), contains("Per")) %>%
    gather(Stat, Value) %>%
    mutate(Stat = as.factor(Stat)) %>%
    merge(data[,c("Stat","order")],by="Stat") %>%
    arrange(order)

  data$Stat = factor(data$Stat, levels = data$Stat[order(data$order, decreasing = FALSE)], ordered=TRUE,
                     labels = c("Points","effFG%","FG%","FG_A","FG_M","FG_2P%","FG_2PM","FG_2PA","FG_3P%","FG_3PM","FG_3PA","FT%","FT_M","FT_A","AST","TRB","DRB","ORB","STL","BLK","TOV","PF"))

  maxs$Stat = factor(maxs$Stat, levels = maxs$Stat[order(data$order, decreasing = FALSE)], ordered=TRUE,
                     labels = c("Points","effFG%","FG%","FG_A","FG_M","FG_2P%","FG_2PM","FG_2PA","FG_3P%","FG_3PM","FG_3PA","FT%","FT_M","FT_A","AST","TRB","DRB","ORB","STL","BLK","TOV","PF"))

  ggplot(NULL) +
    geom_bar(data = data, aes(Stat, Value), stat = "identity", fill=factor(data$color)) +
    geom_bar(data = maxs, aes(Stat, Value), stat = "identity", fill = "grey", alpha = 0.3) +
    #coord_flip() +
    geom_text(data = data, aes(Stat,0.95,label = ifelse(grepl("%",Stat), paste0(round(Value*100,1),"%"),
                          ifelse(grepl("Usage",Stat), paste0(round(Value*1000,1),"%"),round(Value,2))))) +
    geom_text(data = data, aes(Stat,.85,label = paste0("(",Rank,")"))) +
    theme(legend.key=element_blank(),
              legend.title=element_blank(),
              legend.text = element_blank(),
              legend.position="none",
              plot.title = element_text(size=9),
              panel.border = element_blank(),
              panel.background = element_blank(),
              axis.text.x = element_text(size = 8),
              #axis.text.y = element_blank(),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank())

})

renderPlot(barplotTeamStats())

```

### Similar Teams
```{r}

similarTeams <- reactive({

  if (input$bubble_size == "yes") useEffMin <- TRUE else useEffMin <- FALSE
  
  similar_teams <- select(values$teamsTSNE,Tm,x,y) %>%
    group_by(Tm) %>%
    mutate(dist = BC_distance(values$playersTSNE,values$playersDatabase,input$teamCode,Tm,input$num_clusters,useEffMin)) %>% arrange(dist) %>% select(-x,-y) %>% top_n(30,-dist) %>% filter(!(Tm == input$teamCode)) %>%
    merge(values$teamsDatabase[,c("Tm","TeamOffense","TeamDefense","wins")], by="Tm") %>%
    mutate(Offense = round(TeamOffense,1), Defense = round(TeamDefense,1),wins = round(wins,1),dist = round(dist,5)) %>%
    arrange(dist) %>%
    select(Team = Tm, Offense, Defense, wins, `Bhattacharyya dist` = dist)
  
  datatable(similar_teams,extensions = c('Scroller'),
            options = list(dom='t',
                           pageLength = 30,
                           autoWidth = TRUE,
                           #deferRender = TRUE,
                           scrollY = 450,
                           #scrollX = TRUE,
                           #fixedColumns = list(leftColumns = 1),
                           scroller = TRUE,
                           initComplete = JS("function(settings, json) {","$(this.api().table().header()).css({'background-color': '#fff', 'color': '#575859', 'font-size': '10px', 'font-weight': 'bold'});","}")),
            rownames = FALSE) %>%
    formatRound(c('Offense','Defense'), 2) %>%
    formatStyle(0, target = 'row', fontSize = '70%', lineHeight = '70%')
})

renderDataTable(similarTeams())

```

### Roster
```{r}

roster <- reactive({
  #roster <- filter(playerDashboard, Tm == "ATL") %>%
  roster <- filter(values$playersDatabase, Tm == input$teamCode) %>%
    merge(select(values$playersRanks,Player,rank_Off = Offense,rank_Def = Defense), by="Player") %>%
    mutate(rank_Def = nrow(values$playersDatabase) - rank_Def - 1) %>%
    arrange(desc(effMin)) %>%
    mutate(Usage = paste0(round(effMin*1000,1),"%")) %>%
    select(Player,Pos,Age,Exp,Offense,Defense,Usage,rank_Off,rank_Def)

  datatable(roster, options = list(dom="t", pageLength = 25,initComplete = JS("function(settings, json) {","$(this.api().table().header()).css({'background-color': '#fff', 'color': '#575859', 'font-size': '10px', 'font-weight': 'bold'});","}")), rownames = FALSE) %>%
    formatStyle('Offense', valueColumns='rank_Off', color = JS(paste0("value < ",nrow(values$playersRanks)/3," ? 'green' : value < ",nrow(values$playersRanks)*2/3," ? 'lightblue' : 'red'")), fontWeight = 'bold') %>%
    formatStyle('Defense', valueColumns='rank_Def', color = JS(paste0("value < ",nrow(values$playersRanks)/3," ? 'green' : value < ",nrow(values$playersRanks)*2/3," ? 'lightblue' : 'red'")), fontWeight = 'bold') %>%
    formatRound(c('Offense','Defense'), 2) %>%
    formatStyle(c('Exp','Usage'), textAlign = 'right') %>%
    formatStyle(0, target = 'row', fontSize = '70%', lineHeight = '70%')

})

renderDataTable(roster())

```

### Team t-SNE map
```{r}
tsne_teamPredicted <- reactive({

  set.seed(456)
  #playerCluster <- kmeans(tsne_ready[, c("x","y")], 13, nstart = 10, iter.max = 20)
  playerCluster <- kmeans(values$playersTSNE[, c("x","y")], input$num_clusters, nstart = 10, iter.max = 20)
  tsne_ready2 <- cbind(values$playersTSNE, K_means = playerCluster$cluster) %>%
    merge(values$playersDatabase[,c("Player","effMin","Offense","Defense")], by="Player") %>%
    mutate(Defense = -Defense)

  #tsne_points_filter <- filter(tsne_ready2, Tm == "ATL")
  tsne_points_filter <- filter(tsne_ready2, Tm == input$teamCode)
    #centroid <- data.frame(x=(mean(tsne_points_filter$x)),y=mean(tsne_points_filter$y))
    #x_limit <- c(min(tsne_points_filter$x)-5,max(tsne_points_filter$x)+10)
    #y_limit <- c(min(tsne_points_filter$y)-5,max(tsne_points_filter$y)+10)

  cluster_representative <- group_by(tsne_ready2, K_means) %>%
    mutate(x_mean = mean(x), y_mean=mean(y)) %>%
    mutate(dist = sqrt((x-x_mean)^2+(y-y_mean)^2)) %>%
    filter(dist==min(dist)) %>%
    select(K_means, Player,Season, x,y,dist) %>%
    ungroup()

  if (input$bubble_size == "yes") size_balloons <- "effMin*10" else size_balloons <- 5

  if (nrow(tsne_points_filter) > 0) {
    if (!(input$team_tsne_color == "K_means")) {
      ggplot(NULL, aes(x,y)) +
        geom_point(data=tsne_ready2,aes(color = eval(parse(text=input$team_tsne_color))),alpha = 0.6) +
        geom_point(data=tsne_points_filter,aes(color = eval(parse(text=input$team_tsne_color)), size=eval(parse(text = size_balloons))),alpha = 1) +
        scale_color_gradient2(midpoint = eval(parse(text = paste0("median(as.numeric(tsne_ready2$",input$team_tsne_color,"))"))), low="red", mid="white",high="green")+
        geom_text(data = cluster_representative, aes(label = paste0(Player," (",Season,")")),size=3, nudge_y = 1, color = 'lightgrey') +
        geom_text(data=tsne_points_filter,aes(label = paste0(Player," (",Season,")")),size=3, nudge_y = 1, color = 'blue') +
        theme(legend.key=element_blank(),
              legend.title=element_blank(),
              legend.text = element_blank(),
              legend.position="none",
              plot.title = element_text(size=9),
              panel.border = element_blank(),
              panel.background = element_blank(),
              axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank())
    } else {
      ggplot(NULL, aes(x,y)) +
        geom_point(data=tsne_ready2,aes(color = as.factor(K_means)),alpha = 0.6) +
        geom_point(data=tsne_points_filter,aes(color = as.factor(K_means), size=eval(parse(text = size_balloons))),alpha = 1) +
        geom_text(data = cluster_representative, aes(label = paste0(Player," (",K_means,")")),size=3, nudge_y = 1, color = 'lightgrey') +
        geom_text(data=tsne_points_filter,aes(label = paste0(Player," (",K_means,")")),size=3, nudge_y = 1, color = 'blue') +
        theme(legend.key=element_blank(),
              legend.title=element_blank(),
              legend.text = element_blank(),
              legend.position="none",
              plot.title = element_text(size=9),
              panel.border = element_blank(),
              panel.background = element_blank(),
              axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank())
    }

  } else {
    ggplot(NULL, aes(x,y)) +
        geom_point(data=tsne_ready2,aes(color = K_means),alpha = 1) +
        scale_color_gradient2(midpoint = median(tsne_ready2$K_means), low="red", mid="white",high="green")+
        geom_text(data = cluster_representative, aes(label = paste0(Player," (",K_means,")")),size=3, nudge_y = 1, color = 'lightgrey') +
        theme(legend.key=element_blank(),
              legend.title=element_blank(),
              legend.text = element_blank(),
              legend.position="none",
              plot.title = element_text(size=9),
              panel.border = element_blank(),
              panel.background = element_blank(),
              axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank())
  }

})

renderPlot(tsne_teamPredicted())
```

### Facet t-SNE maps
```{r}
tsne_teamPredicted_facets <- reactive({

  set.seed(456)
  playerCluster <- kmeans(values$playersTSNE[, c("x","y")], input$num_clusters, nstart = 10, iter.max = 20)
  tsne_ready2 <- cbind(values$playersTSNE, cluster = playerCluster$cluster) %>%
    merge(values$playersDatabase[,c("Player","Tm","effMin","Offense","Defense")], by=c("Player","Tm")) %>%
    mutate(Defense = -Defense)

  if (input$bubble_size == "yes") size_balloons <- "effMin*10" else size_balloons <- 5

  if (!(input$team_tsne_color == "K_means")) {
    ggplot(data=tsne_ready2, aes(x,y)) +
      #geom_point(data=tsne_ready2,aes(color = as.factor(cluster)),alpha = 0.2) +
      geom_point(data=tsne_ready2,aes(color = eval(parse(text=input$team_tsne_color)), size=eval(parse(text = size_balloons)))) +
      #geom_text(data=tsne_ready2,aes(label = paste0(Player," (",Season,")")),size=3, nudge_y = 1) +
      scale_color_gradient2(midpoint = eval(parse(text = paste0("median(as.numeric(tsne_ready2$",input$team_tsne_color,"))"))),low="red",mid="white",high="green") +
      theme(legend.position = "right", legend.title = element_blank()) +
      facet_wrap(~Tm) +
       theme( plot.title = element_text(size=9),
              panel.border = element_blank(),
              panel.background = element_blank(),
              axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank())
  } else {
    ggplot(data=tsne_ready2, aes(x,y)) +
      #geom_point(data=tsne_ready2,aes(color = as.factor(cluster)),alpha = 0.2) +
      geom_point(data=tsne_ready2,aes(color = as.factor(cluster),size=eval(parse(text = size_balloons)))) +
      #geom_text(data=tsne_ready2,aes(label = paste0(Player," (",Season,")")),size=3, nudge_y = 1) +
      theme(legend.position = "right", legend.title = element_blank()) +
      labs(fill='Usage') +
      facet_wrap(~Tm) +
       theme( plot.title = element_text(size=9),
              panel.border = element_blank(),
              panel.background = element_blank(),
              axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank())
  }

})

renderPlot(tsne_teamPredicted_facets())
```

### Cluster detail
```{r}
cluster_detail <- reactive({

  set.seed(456)
  #playerCluster <- kmeans(tsne_ready[, c("x","y")], 10, nstart = 10, iter.max = 20)
  playerCluster <- kmeans(values$playersTSNE[, c("x","y")], input$num_clusters, nstart = 10, iter.max = 20)
  
  cluster_detail <- cbind(values$playersTSNE, cluster = playerCluster$cluster) %>%
    merge(select(values$playersDatabase, -c(Pos,Season,Exp)), by=c("Player","Tm")) %>%
    group_by(cluster) %>%
    summarise_if(is.numeric, mean)
  
  cluster_ranks <- mutate_if(cluster_detail,is.numeric, function(x) row_number(desc(x))) %>%
    mutate(cluster = nrow(cluster_detail)-cluster + 1, Defense = nrow(cluster_detail)-Defense + 1, effTOV = nrow(cluster_detail)-effTOV + 1, effPF = nrow(cluster_detail)-effPF + 1)
  
  names(cluster_ranks) <- paste0("rank_",names(cluster_ranks))
  names(cluster_ranks)[1] <- "cluster"
  
  cluster_detail2 <- merge(cluster_detail, cluster_ranks, by = "cluster")
  
  datatable(cluster_detail2, extensions = c('Scroller','FixedColumns'), options = list(dom="t",pageLength = nrow(cluster_detail), 
                           autoWidth = TRUE,
                           deferRender = TRUE,
                           scrollY = 200,
                           scrollX = TRUE,
                           fixedColumns = list(leftColumns = 1),
                           scroller = TRUE,
                           initComplete = JS("function(settings, json) {","$(this.api().table().header()).css({'background-color': '#fff', 'color': '#575859', 'font-size': '10px', 'font-weight': 'bold'});","}"), columnDefs = list(list(visible=FALSE, targets=c(32:62)))), rownames = FALSE,escape = FALSE) %>%
    #formatStyle(c('Defense','effTOV','effPF'), valueColumns=c('rank_Defense','rank_effTOV','rank_effPF'), color = JS(paste0("value < ",nrow(cluster_detail)/3," ? 'red' : value < ",nrow(cluster_detail)*2/3," ? 'lightblue' : 'green'")), fontWeight = 'bold') %>%
    formatStyle(c(5:32), valueColumns=c(36:63), color = JS(paste0("value < ",nrow(cluster_detail)/3," ? 'green' : value < ",nrow(cluster_detail)*2/3," ? 'lightblue' : 'red'")), fontWeight = 'bold') %>%
    formatRound(c(2:32), 3) %>%
    #formatStyle(c('Exp','Usage'), textAlign = 'right') %>%
    formatStyle(0, target = 'row', fontSize = '70%', lineHeight = '70%')

  
})

cluster_color_team <- reactive({

  set.seed(456)
  playerCluster <- kmeans(values$playersTSNE[, c("x","y")], input$num_clusters, nstart = 10, iter.max = 20)
  tsne_ready2 <- cbind(values$playersTSNE, cluster = playerCluster$cluster) %>%
    merge(values$playersDatabase[,c("Player","Tm","effMin","Offense","Defense")], by=c("Player","Tm")) %>%
    mutate(Defense = -Defense) %>%
    filter(Tm == input$teamCode)

  if (input$bubble_size == "yes") size_balloons <- "effMin*10" else size_balloons <- 5

  if (!(input$team_tsne_color == "K_means")) {
    ggplot(data=tsne_ready2, aes(x,y)) +
      #geom_point(data=tsne_ready2,aes(color = as.factor(cluster)),alpha = 0.2) +
      geom_point(data=tsne_ready2,aes(color = eval(parse(text=input$team_tsne_color)), size=eval(parse(text = size_balloons)))) +
      geom_text(data=tsne_ready2,aes(label = Player),size=3, nudge_y = 3) +
      scale_color_gradient2(midpoint = eval(parse(text = paste0("median(as.numeric(tsne_ready2$",input$team_tsne_color,"))"))),low="red",mid="white",high="green") +
      theme(legend.position = "right", legend.title = element_blank()) +
      #facet_wrap(~Tm) +
       theme( plot.title = element_text(size=9),
              panel.border = element_blank(),
              panel.background = element_blank(),
              axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank())
  } else {
    ggplot(data=tsne_ready2, aes(x,y)) +
      #geom_point(data=tsne_ready2,aes(color = as.factor(cluster)),alpha = 0.2) +
      geom_point(data=tsne_ready2,aes(color = as.factor(cluster),size=eval(parse(text = size_balloons)))) +
      geom_text(data=tsne_ready2,aes(label = paste0(Player," (",cluster,")")),size=3, nudge_y = 1) +
      theme(legend.position = "right", legend.title = element_blank()) +
      #labs(fill='Usage') +
      #facet_wrap(~Tm) +
       theme( plot.title = element_text(size=9),
              panel.border = element_blank(),
              panel.background = element_blank(),
              axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank())
  }

})

team_cluster_detail <- reactive({

  set.seed(456)
  #playerCluster <- kmeans(tsne_ready[, c("x","y")], 10, nstart = 10, iter.max = 20)
  playerCluster <- kmeans(values$playersTSNE[, c("x","y")], input$num_clusters, nstart = 10, iter.max = 20)
  
  cluster_detail <- cbind(values$playersTSNE, cluster = playerCluster$cluster) %>%
    merge(select(values$playersDatabase, -c(Pos,Season,Exp)), by=c("Player","Tm")) %>%
    filter(Tm == input$teamCode) %>%
    mutate(total_players = length(Player), total_min = sum(effMin)) %>%
    group_by(cluster) %>%
    mutate(percent = n_distinct(Player)/total_players, percent_usage = sum(effMin)/total_min) %>%
    distinct(cluster, percent, percent_usage) %>%
    arrange(cluster)
  
  datatable(cluster_detail, extensions = c('Scroller'), options = list(dom="t",pageLength = nrow(cluster_detail), 
                           #autoWidth = TRUE,
                           #deferRender = TRUE,
                           scrollY = 200,
                           #scrollX = TRUE,
                           #fixedColumns = list(leftColumns = 1),
                           scroller = TRUE,
                           initComplete = JS("function(settings, json) {","$(this.api().table().header()).css({'background-color': '#fff', 'color': '#575859', 'font-size': '10px', 'font-weight': 'bold'});","}")), rownames = FALSE,escape = FALSE) %>%
    formatPercentage(c(2,3),digits = 1) %>%
    formatStyle(0, target = 'row', fontSize = '70%', lineHeight = '70%')
  
})

fluidPage(
  fluidRow(
    column(8,div(renderPlot(cluster_color_team()),style="height:250px;")),
    column(4,div(renderDataTable(team_cluster_detail()),style="height:250px;"))
  ),
  fluidRow(
    column(12,renderDataTable(cluster_detail()))
  )
)

```

### Team Ranks
```{r}

allTeams <- reactive({
  
  teamRanks2 <- values$teamsRanks
  teamDashboard2 <- values$teamsDatabase
  #teamRanks2 <- teamRanks
  #teamDashboard2 <- teamDashboard
  
  names(teamRanks2)[-1] <- paste0("rank_",names(teamRanks2)[-1])
  names(teamDashboard2)[-1] <- paste0("stat_",names(teamDashboard2)[-1])
  
  data <- merge(teamDashboard2,
                select(teamRanks2,Tm,rank_TeamOffense,rank_TeamDefense,rank_wins), by = "Tm") 
  
  data <- select(data, Tm, Offense = stat_TeamOffense, Defense = stat_TeamDefense, wins = stat_wins, starts_with("rank"),-stat_Season) %>%
    as.data.frame()
  
datatable(data, extensions = c('Scroller'), options = list(dom="t",pageLength = nrow(data), 
                         scrollY = 450,
                         scroller = TRUE,
                         initComplete = JS("function(settings, json) {","$(this.api().table().header()).css({'background-color': '#fff', 'color': '#575859', 'font-size': '10px', 'font-weight': 'bold'});","}"), columnDefs = list(list(visible=FALSE, targets=c(4:6)))), rownames = FALSE) %>%
  formatStyle(c('Defense'), valueColumns=c('rank_TeamDefense'), color = JS(paste0("value < ",nrow(data)/3," ? 'red' : value < ",nrow(data)*2/3," ? 'lightblue' : 'green'")), fontWeight = 'bold') %>%
  formatStyle(c(2:4), valueColumns=c(5:7), color = JS(paste0("value < ",nrow(data)/3," ? 'green' : value < ",nrow(data)*2/3," ? 'lightblue' : 'red'")), fontWeight = 'bold') %>%
  formatRound(c(2:4), 1) %>%
  formatStyle(0, target = 'row', fontSize = '70%', lineHeight = '70%')
  
})

renderDataTable(allTeams()) 
```

Season
=====================================

Row {.sidebar}
-----------------------------------------------------------------------

```{r}
selectizeInput('regSeasonDay', 'Select a day:', choices=datesRange, selected = datesRange[1])

```

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Game Probabilities
```{r}
games_probs <- reactive({
  predGames <- .getGameProbability("W",input$regSeasonDay)
  names(predGames) <- c("Game","Away","Home","Prob. Home team wins")
  datatable(predGames,extensions = c('Scroller'),
            options = list(dom='t',
                           pageLength = 15,
                           autoWidth = TRUE,
                           #deferRender = TRUE,
                           scrollY = 500,
                           #scrollX = TRUE,
                           #fixedColumns = list(leftColumns = 1),
                           scroller = TRUE,
                           initComplete = JS("function(settings, json) {","$(this.api().table().header()).css({'background-color': '#fff', 'color': '#575859', 'font-size': '10px', 'font-weight': 'bold'});","}")),
            rownames = TRUE) %>%
    formatRound(c('Away','Home'), 0) %>%
    formatRound(c(ncol(predGames)), 2) %>%
    formatStyle(0, target = 'row', fontSize = '70%', lineHeight = '70%')
})

# reg season games
renderDataTable(games_probs())
```

### Standings
```{r}

standingsW_table <- reactive({
  stands <- .getConferenceStandings("W",input$regSeasonDay)
  
  datatable(stands,extensions = c('Scroller'),
            options = list(dom='t',
                           pageLength = 30,
                           autoWidth = TRUE,
                           #deferRender = TRUE,
                           scrollY = 250,
                           #scrollX = TRUE,
                           #fixedColumns = list(leftColumns = 1),
                           scroller = TRUE,
                           initComplete = JS("function(settings, json) {","$(this.api().table().header()).css({'background-color': '#fff', 'color': '#575859', 'font-size': '10px', 'font-weight': 'bold'});","}")),
            rownames = TRUE) %>%
    #formatRound(c('Offense','Defense'), 2) %>%
    formatStyle(0, target = 'row', fontSize = '70%', lineHeight = '70%')
  
  
})
### Standings East
standingsE_table <- reactive({
  stands <- .getConferenceStandings("E",input$regSeasonDay)
  
  datatable(stands,extensions = c('Scroller'),
            options = list(dom='t',
                           pageLength = 30,
                           autoWidth = TRUE,
                           #deferRender = TRUE,
                           scrollY = 250,
                           #scrollX = TRUE,
                           #fixedColumns = list(leftColumns = 1),
                           scroller = TRUE,
                           initComplete = JS("function(settings, json) {","$(this.api().table().header()).css({'background-color': '#fff', 'color': '#575859', 'font-size': '10px', 'font-weight': 'bold'});","}")),
            rownames = TRUE) %>%
    #formatRound(c('Offense','Defense'), 2) %>%
    formatStyle(0, target = 'row', fontSize = '70%', lineHeight = '70%')
})

fluidPage(
  fluidRow(
    column(12,div(renderDataTable(standingsE_table()),style="height:280px;"))
  ),
  fluidRow(
    column(12,div(renderDataTable(standingsW_table()),style="height:280px;"))
  )
)

```

### Probability Matrix
```{r}
win_probs <- reactive({
  stands <- .winProbability_matrix()
  datatable(stands,extensions = c('Scroller','FixedColumns'),
            options = list(dom='t',
                           pageLength = 30,
                           autoWidth = TRUE,
                           #deferRender = TRUE,
                           scrollY = 550,
                           scrollX = TRUE,
                           fixedColumns = list(leftColumns = 1),
                           scroller = TRUE,
                           initComplete = JS("function(settings, json) {","$(this.api().table().header()).css({'background-color': '#fff', 'color': '#575859', 'font-size': '10px', 'font-weight': 'bold'});","}")),
            rownames = FALSE) %>%
    formatRound(c(2:ncol(stands)), 2) %>%
    formatStyle(0, target = 'row', fontSize = '70%', lineHeight = '70%')
})

renderDataTable(win_probs())

```

Model
======================================

Row {.sidebar}
-----------------------------------------------------------------------

```{r}
selectizeInput("nnet", "Select Neural Net", choices = c("Offense","Defense"), selected = "Offense")

selectizeInput("layer", "Select layer:", choices = c(1:3), selected = 1)

```

Row
----------------------------------------

### Neural Network
```{r, fig.height=6,fig.width=6}

# Create pdf plots by running these:
# plot(nn_Defense, arrow.length = .15, col.entry = "red", col.out = "green", fontsize = 9, dimension = 10)
# plot(nn_Offense, arrow.length = .15, col.entry = "red", col.out = "green", fontsize = 9, dimension = 10)
# Then open with preview and export as .PNG into images/

selectNNet <- reactive({

  filename <- normalizePath(file.path('./images/',
                              paste('nnet_', input$nnet, '.png', sep='')))
  # Return a list containing the filename
    list(src = filename,
         width = '100%',
         height = '100%')
})

renderImage({
    selectNNet()
  }, deleteFile = FALSE)

```

### Weights
```{r}

table_weight <- reactive({
  
  if (input$nnet == "Offense") {
    model <- nn_Offense
    load("data/modelNeuralnet5_PTS.Rdata")
    Off_or_Def <- "PTS"
  } else {
     model <- nn_Defense
     load("data/modelNeuralnet5_PTSA.Rdata")
     Off_or_Def <- "PTSA"
  }
  
  if (as.numeric(input$layer) == 1) { # first layer
    #weights <- as.data.frame(model$finalModel$weights[[1]][as.numeric("1")]) %>%
    weights <- as.data.frame(model$finalModel$weights[[1]][as.numeric(input$layer)]) %>%
      cbind(`Source neuron` = c("Intercept",model$finalModel$xNames)) %>%
      select(`Source neuron`, everything())
  } else {
    #weights <- as.data.frame(model$finalModel$weights[[1]][as.numeric("2")]) %>%
    weights <- as.data.frame(model$finalModel$weights[[1]][as.numeric(input$layer)]) %>%
      cbind(`Source neuron` = c("Intercept",names(as.data.frame(model$finalModel$weights[[1]][as.numeric(input$layer)-1])))) %>%
      mutate(`Source neuron` = gsub("X","Neuron_",`Source neuron`)) %>%
      select(`Source neuron`, everything())
  }
  names(weights) <- gsub("X","Neuron_",names(weights))
  
  datatable(weights,extensions = c('Scroller','FixedColumns'),
            options = list(dom='t',
                           pageLength = 15,
                           autoWidth = TRUE,
                           #deferRender = TRUE,
                           scrollY = 250,
                           scrollX = TRUE,
                           fixedColumns = list(leftColumns = 1),
                           scroller = TRUE,
                           initComplete = JS("function(settings, json) {","$(this.api().table().header()).css({'background-color': '#fff', 'color': '#575859', 'font-size': '10px', 'font-weight': 'bold'});","}")),
            rownames = FALSE) %>%
    formatRound(c(2:ncol(weights)), 3) %>%
    formatStyle(0, target = 'row', fontSize = '70%', lineHeight = '70%')

})

renderDataTable(table_weight())

```

Row
----------------------------------

### Best Fit
```{r}
fitPlot <- reactive({
  if (input$nnet == "Offense") {
    model <- nn_Offense
    load("data/modelNeuralnet5_PTS.Rdata")
    Off_or_Def <- "PTS"
  } else {
     model <- nn_Defense
     load("data/modelNeuralnet5_PTSA.Rdata")
     Off_or_Def <- "PTSA"
  }

  playersSumm <- .prepareModel(Off_or_Def)
  ## Strip linearly relationed columns: FG, FGA, FG%,3P%,2P%,FT%,effFG%, effPTS
  playersSumm <- select(playersSumm, -contains("Per"), -effFG, -effFGA, -effPTS, -effTRB)
  ## End of Strip
  scaleMaxMin <- .getScaleLimits(Off_or_Def, data = playersSumm)
  # scale the data [0,1] for easier convergence of backpropagation algorithm
  maxs <- scaleMaxMin$maxs
  mins <- scaleMaxMin$mins

  team_season <- playersSumm[,1]
  scaled <- as.data.frame(scale(playersSumm[,-1], center = mins, scale = maxs - mins))
  scaled <- cbind(team_season,scaled)

  ###
  set.seed(456)
  perc <- 0.75
  train_split <- round(perc*nrow(playersSumm))

  teams_train <- sample(playersSumm$team_season,train_split)
  teams_test <- filter(playersSumm, !(team_season %in% teams_train))$team_season
  training <- filter(scaled, team_season %in% teams_train)
  testing <- filter(scaled, team_season %in% teams_test)

  # remove non-numeric variables
  train_teamSeasonCodes <- training$team_season
  test_teamSeasonCodes <- testing$team_season
  training <- training[,-1]
  testing <- testing[,-1]

  # model already trained (loaded as model above)
  predict_data <- testing
  predicted <- predict(model, newdata = predict_data)
  predictions <- data.frame(actual_PTS = predict_data$PTS, predicted_PTS = predicted)
  plot(predictions)

})

renderPlot(fitPlot())

```


### Model
```{r}

thisModel <- reactive({
  if (input$nnet == "Offense") load("data/modelNeuralnet5_PTS.Rdata") else load("data/modelNeuralnet5_PTSA.Rdata")
  datatable(model$results,
            extensions = c('Scroller','FixedColumns'),
            options = list(dom='t',
                           pageLength = nrow(model$results),
                           autoWidth = TRUE,
                           deferRender = TRUE,
                           scrollY = 250,
                           scrollX = TRUE,
                           fixedColumns = list(leftColumns = 3),
                           scroller = TRUE,
                           initComplete = JS("function(settings, json) {","$(this.api().table().header()).css({'background-color': '#fff', 'color': '#575859', 'font-size': '10px', 'font-weight': 'bold'});","}")),
            rownames = FALSE) %>%
    formatStyle(0, target = 'row', fontSize = '60%', lineHeight = '80%') %>%
    formatRound(c(4:ncol(model$results)),digits = 3)
})

renderDataTable(thisModel())

```

<!-- ### Probability Distribution -->

<!-- $\Large{X \sim \mathrm{N}(\hat{\mu}_O,\hat{\sigma})}$ -->

Empirical evidence
======================================

```{r}
avg_points <- mutate(gameScores, pts_home = as.numeric(pts_home), pts_away = as.numeric(pts_away)) %>%
  filter(!is.na(pts_home), !is.na(pts_away))

```

Row {.sidebar}
-----------------------------------------------------------------------

```{r}
sliderInput("pastSeasons", "Select Number of Seasons:", min = 1, max = 20, value = 5)

```

Row
-------------------------

### Normal Hyperparameters
$\hat{\sigma}$ = `r round(sigma,2)`

$\hat{\mu}_H$ = `r round(avgHome,2)`

$\hat{\mu}_A$ = `r round(avgAway,2)`

$\hat{\mu}$ = `r round(global_mean,2)`

${HomeAwayFactor = \hat{\mu}_H - \hat{\mu}_A}$ = `r round(home_away_factor,2)`

### Means
```{r}

ggplot(avg_points) +
  geom_density(aes(x=pts_home), fill = "lightblue", alpha = .3) +
  geom_vline(xintercept = avgHome, show.legend = round(avgHome,2), color = "blue") +
  geom_text(aes(x = avgHome+5,y = -0.005,label = round(avgHome,2))) +
  geom_density(aes(x=pts_away), fill = "pink", alpha = .3) +
  geom_vline(xintercept = avgAway, show.legend = round(avgAway,2), color = "red") +
  geom_text(aes(x = avgAway-5, y = -0.005, label = round(avgAway,2))) +
  theme( plot.title = element_text(size=9),
              panel.border = element_blank(),
              panel.background = element_blank(),
              #axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.title.x = element_blank(),
              axis.title.y = element_blank(),
              axis.ticks = element_blank())

```

Row
----------------------

### College to NBA minute reduction by draft pick
```{r}
collegePlayersHist <- read.csv("data/collegePlayersHist.csv", stringsAsFactors = FALSE)
rookiesDraftHist <- read.csv("data/rookiesDraftHist.csv", stringsAsFactors = FALSE)
# compute % minutes played per player:
collegeMinutes <- merge(collegePlayersHist,rookiesDraftHist[,c("Player","Pick","Year")], by = "Player") %>%
  mutate(perMin = MP/(G*40)) %>%
  group_by(Player) %>%
  mutate(perMin = mean(perMin, na.rm=TRUE)) %>% # average minutes played per game in ther college years
  distinct(Player, .keep_all=TRUE) %>%
  filter(!is.na(perMin))
# now do the same for NBA players by experience year
nbaMinutes <- select(playersHist, Player,Season,Age,Tm,G,MP) %>%
  filter(!(Tm == "TOT")) %>%
  group_by(Player) %>%
  filter(Age == min(Age)) %>% # keep players when they were younger (rookie year)
  group_by(Player,Season) %>%
  filter(G >= 30) %>% # played at least 30 games
  mutate(perMin = mean(MP, na.rm=TRUE)/48) %>%
  distinct(Player, .keep_all=TRUE)
# put them together
college2nbaMinutes <- merge(nbaMinutes,collegeMinutes, by = "Player", all.x = TRUE) %>%
  mutate(minDiff = perMin.y-perMin.x) %>%
  filter(!is.na(minDiff))
# see if there is correlation between player Rank and effMin of play from college to NBA
#plot(college2nbaMinutes$Rk,college2nbaMinutes$minDiff, xlim = c(0,100))
# no clear pattern so I will use the average for simplification.
# Although Rank is different from Draft pick. Let's see this by draft pick for the top 30 picks:
#plot(college2nbaMinutes$Pick,college2nbaMinutes$minDiff)
draftMinutesInNBA <- arrange(college2nbaMinutes, desc(Pick)) %>%
  group_by(Pick) %>%
  summarise(mean(minDiff)) %>%
  mutate(Pick = as.numeric(Pick)) %>%
  arrange(Pick)

ggplot(draftMinutesInNBA, aes(Pick, `mean(minDiff)`)) +
  geom_bar(stat = "identity") +
  theme( plot.title = element_text(size=9),
              panel.border = element_blank(),
              panel.background = element_blank(),
              #axis.text.x = element_blank(),
              #axis.text.y = element_blank(),
              #axis.title.x = element_blank(),
              #axis.title.y = element_blank(),
              axis.ticks = element_blank())

```

### Distribution of play time
```{r}
plotDistribTime <- reactive({

  topMinShare <- .minutes_density(playersHist,input$pastSeasons)
  averageShare <- group_by(topMinShare,Season) %>%
    summarise_if(is.numeric, mean) %>%
    ungroup() %>%
    summarise_if(is.numeric, mean)
  incrementShare <- gather(averageShare,top_n,percent)

  datatable(incrementShare, extensions = 'Scroller', options = list(dom="t",scrollY = 250,
                           scroller = TRUE), rownames = FALSE) %>%
    formatStyle(0, target = 'row', fontSize = '60%', lineHeight = '70%') %>%
    formatRound(c('percent'), digits = 2)

})

renderDataTable(plotDistribTime())

```

<!-- ### Distribution of play time -->
<!-- ```{r} -->
<!-- plotDistribTime <- reactive({ -->

<!--   topMinShare <- .minutes_density(playersHist,input$pastSeasons) -->
<!--   averageShare <- group_by(topMinShare,Season) %>% -->
<!--     summarise_if(is.numeric, mean) %>% -->
<!--     ungroup() %>% -->
<!--     summarise_if(is.numeric, mean) -->
<!--   incrementShare <- gather(averageShare,top_n,percent) -->

<!--   plot(seq(18,1,-1),incrementShare$percent, xlab = "top n players", ylab = paste0("Accumulated % time (last ",input$pastSeasons,")")) -->

<!-- }) -->

<!-- renderPlot(plotDistribTime()) -->

<!-- ``` -->

t-SNE explorer
======================================

Row {.sidebar}
-----------------------------------------------------------------------

```{r}

sliderInput("tsne_num_clusters", "Number of clusters", min = 2, max = 100, value = 10)
selectizeInput('colSeason', 'Season:', choices=c("All",seasons_list),selected="All",multiple=TRUE,options = list(maxItems = 10,dropdownParent = 'body'))
selectizeInput('colTeam', 'Team:', choices=c("All",teams_list),selected="All",multiple=TRUE,options = list(maxItems = 10,dropdownParent = 'body'))
selectizeInput('colPlayer', 'Player:', choices=c("All",players_list),selected="All",multiple=TRUE,options = list(maxItems = 20,dropdownParent = 'body'))
selectizeInput('colAge', 'Age:', choices=c("All",ages_list),selected="All",multiple=TRUE,options = list(maxItems = 10,dropdownParent = 'body'))

HTML('<hr style="color: purple;">')
h4("Color by")
selectizeInput('colSkill', 'Skill:', choices=c("K-means",skills_list),selected="K-means",multiple=FALSE)
HTML('<hr style="color: purple;">')

```

Row
-----------------------------------------------------------------------

### t-SNE
```{r}
plotOutput('plotTSNE', 
                  hover = hoverOpts("plot_hover", delay = 100, delayType = "debounce"),
                  click = clickOpts("plot_click"),
                  brush = "plot_brush",
                  dblclick = "plot_dblclick"
           )
uiOutput("hover_info")
uiOutput("click_info")

# server
# Plot tSNE ---------------------
# Single zoomable plot (on left)
ranges <- reactiveValues(x = NULL, y = NULL)

output$plotTSNE <- renderPlot({
  plotTSNE <- .tSNE_plot_All(data = tsne_ready_hist,input$colTeam,input$colSeason,input$colPlayer,
                             input$colAge,input$colSkill,input$tsne_num_clusters)
  if (!is.null(ranges$x)){
    plotTSNE <- plotTSNE + coord_cartesian(xlim = ranges$x, ylim = ranges$y)
  } else {
    plotTSNE <- plotTSNE + coord_cartesian(xlim = ranges$x, ylim = ranges$y)
  }
    #Sys.sleep(2)
  return(plotTSNE)
})
# When a double-click happens, check if there's a brush on the plot.
# If so, zoom to the brush bounds; if not, reset the zoom.
observeEvent(input$plot_dblclick, {
  brush <- input$plot_brush
  if (!is.null(brush)) {
    ranges$x <- c(brush$xmin, brush$xmax)
    ranges$y <- c(brush$ymin, brush$ymax)
    
  } else {
    ranges$x <- NULL
    ranges$y <- NULL
  }
})

# When a brush happens, check if there's a brush on the plot.
# If so, zoom to the brush bounds; if not, do nothing.
observeEvent(input$plot_brush, {
  brush <- input$plot_brush
  if (!is.null(brush)) {
    ranges$x <- c(brush$xmin, brush$xmax)
    ranges$y <- c(brush$ymin, brush$ymax)
    
  } else {
    ranges$x <- NULL
    ranges$y <- NULL
  }
})

# tooltip hover over scatterplot points: see https://gitlab.com/snippets/16220
output$hover_info <- renderUI({
  hover <- input$plot_hover
  point <- nearPoints(.tSNE_plot_filter(data = tsne_ready_hist,input$colTeam,input$colSeason,input$colPlayer,
                                     input$colAge,input$colSkill), hover, threshold = 2, maxpoints = 1, addDist = TRUE)
  
  if (nrow(point) == 0) return(NULL)
  # calculate point position INSIDE the image as percent of total dimensions
  # from left (horizontal) and from top (vertical)
  left_pct <- (hover$x - hover$domain$left) / (hover$domain$right - hover$domain$left)
  top_pct <- (hover$domain$top - hover$y) / (hover$domain$top - hover$domain$bottom)
  
  # calculate distance from left and bottom side of the picture in pixels
  left_px <- hover$range$left + left_pct * (hover$range$right - hover$range$left)
  top_px <- hover$range$top + top_pct * (hover$range$bottom - hover$range$top)
  
  # create style property fot tooltip
  # background color is set so tooltip is a bit transparent
  # z-index is set so we are sure are tooltip will be on top
  style <- paste0("position:absolute; z-index:100; background-color: rgba(245, 245, 245, 0.85); ",
                  "left:", left_px + 12, "px; top:", top_px + 12, "px;")
  
  # actual tooltip created as wellPanel
  wellPanel(
    style = style,
    p(HTML(paste0(point$Player, "<br/>",point$Tm," - ",point$Season, "(Age: ", point$Age,") ", 
                  "<b> Min: </b>", round(point$effMin,3), 
                  "<b> Pts: </b>", round(point$effPTS,3),
                  "<b> Ast: </b>", round(point$effAST,3), 
                  "<b> ORb: </b>", round(point$effORB,3), 
                  "<b> DRb: </b>", round(point$effDRB,3), 
                  "<b> FT%: </b>", round(point$effFTM/point$effFTA,3),
                  "<b> 3P%: </b>", round(point$eff3PM/point$eff3PA,3),
                  "<b> Stl: </b>", round(point$effSTL,3),
                  "<b> Blk: </b>", round(point$effBLK,3),
                  "<b> Tov: </b>", round(point$effTOV,3),
                  "<b> PFl: </b>", round(point$effPF,3),
                  " <br/>"
                  )))
  )
})

# tooltip click over scatterplot points: see https://gitlab.com/snippets/16220
output$click_info <- renderUI({
  click <- input$plot_click
  point <- nearPoints(.tSNE_plot_filter(data = tsne_ready_hist,input$colTeam,input$colSeason,input$colPlayer,
                                     input$colAge,input$colSkill), click, threshold = 5, maxpoints = 1, addDist = TRUE)
  
  #     
  if (nrow(point) == 0) return(NULL)
  # calculate top 10 closest Country,Period pairs to the clicked one
  tableTop10 <- .compare10_click(data = tsne_ready_hist,point$Season,point$Player)
  # calculate point position INSIDE the image as percent of total dimensions
  # from left (horizontal) and from top (vertical)
  left_pct <- (click$x - click$domain$left) / (click$domain$right - click$domain$left)
  top_pct <- (click$domain$top - click$y) / (click$domain$top - click$domain$bottom)
  
  # calculate distance from left and bottom side of the picture in pixels
  # avoid overlapping with other objects by keeping the tooltip inside the frame
  if (left_pct > .75){
    if (top_pct >.75){
      left_px <- -15*click$range$left + left_pct * (click$range$right - click$range$left)
      top_px <- click$range$top + top_pct * (click$range$bottom - click$range$top)
    } else {
      left_px <- -15*click$range$left + left_pct * (click$range$right - click$range$left)
      top_px <- click$range$top + top_pct * (click$range$bottom - click$range$top)
    }
  } else {
    
    if (top_pct >.75){
      left_px <- click$range$left + left_pct * (click$range$right - click$range$left)
      top_px <- click$range$top + top_pct * (click$range$bottom - click$range$top)
    } else{
      left_px <- click$range$left + left_pct * (click$range$right - click$range$left)
      top_px <- click$range$top + top_pct * (click$range$bottom - click$range$top)
    }
  }
  # create style property fot tooltip
  # background color is set so tooltip is a bit transparent
  # z-index is set so we are sure are tooltip will be on top
  style <- paste0("position:absolute; z-index:10; background-color: rgba(245, 245, 245, 0.85); ",
                  "left:", left_px + 2, "px; top:", top_px + 2, "px;")
  # actual tooltip created as wellPanel
  panel_input <- paste0('Closest 10 Players (Eucl. dist.) to ',tableTop10$Player[1],' in ',tableTop10$Season[1],'</a><br/><br/>')
  for (i in 2:11){
    panel_input <- paste0(panel_input, tableTop10$Player[i],' (',tableTop10$Season[i],') ',round(tableTop10$dist[i],3),'<br/>')
  }
  
  wellPanel(
    style = style,
    p(HTML(panel_input))
  )
})

```

Trade market
======================================

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Trade players
```{r}

allPlayers <- reactive({
  
  #playerRanks <- mutate_if(playerDashboard, is.numeric, function(x) row_number(desc(x)))
  playerRanks2 <- values$playersRanks
  playerDashboard2 <- values$playersDatabase
  names(playerRanks2)[-1] <- paste0("rank_",names(playerRanks2)[-1])
  names(playerDashboard2)[-1] <- paste0("stat_",names(playerDashboard2)[-1])
  
  data <- merge(playerDashboard2,group_by(playerRanks2,Player) %>% select_if(is.numeric) %>% select(-rank_Age), by = "Player") 
  
  # if (input$isRank == "Ranks") {
  #   data <- mutate(data, rank_Defense = nrow(values$playersRanks)-rank_Defense+1, rank_TOV = nrow(values$playersRanks)-rank_TOV+1, rank_PF = nrow(values$playersRanks)-rank_PF+1) %>%
  #     select(Player,Pos = stat_Pos, Age = stat_Age, Team = stat_Tm, Exp = stat_Exp, rank_Offense, rank_Defense, rank_Usage = rank_effMin, starts_with("rank")) %>%
  #     as.data.frame()
  # names(data) <- gsub("rank_","",names(data))
  # 
  # datatable(data, extensions = c('Scroller','FixedColumns'), options = list(dom="ft",pageLength = nrow(model$results), 
  #                          autoWidth = TRUE,
  #                          deferRender = TRUE,
  #                          scrollY = 650,
  #                          scrollX = TRUE,
  #                          fixedColumns = list(leftColumns = 1),
  #                          scroller = TRUE,
  #                          initComplete = JS("function(settings, json) {","$(this.api().table().header()).css({'background-color': '#fff', 'color': '#575859', 'font-size': '10px', 'font-weight': 'bold'});","}")), rownames = FALSE) %>%
  #   formatStyle(c('Exp'), textAlign = 'right') %>%
  #   formatStyle(0, target = 'row', fontSize = '70%', lineHeight = '70%')
  #   
  # } else {
    data <- mutate(data, Usage = paste0(round(stat_effMin*1000,1),"%")) %>%
      select(Player,Pos = stat_Pos, Age = stat_Age, Team = stat_Tm, Exp = stat_Exp, Offense = stat_Offense, Defense = stat_Defense, Usage, starts_with("stat"), rank_Offense, rank_Defense, rank_effMin, starts_with("rank"), -stat_effMin, -stat_Season) %>%
      as.data.frame()
  
    names(data) <- gsub("stat_","",names(data))
    
    # Add the trade buttons  
    data2 <- as.data.frame(cbind(View = shinyInput(actionButton, 
                                                     nrow(data),
                                                     'button_', 
                                                     label = "Trade", 
                                                onclick='Shiny.onInputChange(\"select_button\",this.id)', style = 'padding:2px; width:40px; height:20px; font-size:85%'),
                                 data))
    
  datatable(data2, extensions = c('Scroller','FixedColumns'), options = list(dom="ft",pageLength = nrow(model$results), 
                           autoWidth = TRUE,
                           deferRender = TRUE,
                           scrollY = 650,
                           scrollX = TRUE,
                           fixedColumns = list(leftColumns = 2),
                           scroller = TRUE,
                           initComplete = JS("function(settings, json) {","$(this.api().table().header()).css({'background-color': '#fff', 'color': '#575859', 'font-size': '10px', 'font-weight': 'bold'});","}"), columnDefs = list(list(visible=FALSE, targets=c(34:61)))), rownames = FALSE,escape = FALSE) %>%
    formatStyle(c('Defense','effTOV','effPF'), valueColumns=c('rank_Defense','rank_effTOV','rank_effPF'), color = JS(paste0("value < ",nrow(values$playersRanks)/3," ? 'red' : value < ",nrow(values$playersRanks)*2/3," ? 'lightblue' : 'green'")), fontWeight = 'bold') %>%
    formatStyle(c(7:34), valueColumns=c(35:62), color = JS(paste0("value < ",nrow(values$playersRanks)/3," ? 'green' : value < ",nrow(values$playersRanks)*2/3," ? 'lightblue' : 'red'")), fontWeight = 'bold') %>%
    formatRound(c(7:8,10:34), 3) %>%
    formatStyle(c('Exp','Usage'), textAlign = 'right') %>%
    formatStyle(0, target = 'row', fontSize = '70%', lineHeight = '70%')
  
  #}
  
})

renderDataTable(allPlayers()) 
uiOutput('trade_popup')

observeEvent(input$select_button, {
  toggleModal(session, "modalTrade", "open")
  values$showTradeText <- FALSE
})

SelectedRow <- eventReactive(input$select_button,{
  as.numeric(strsplit(input$select_button, "_")[[1]][2])
})

Selected_Player <- eventReactive(input$select_button,{
  values$playersDatabase[SelectedRow(),1] #column 1 is the group: delivery,agility, .... Column 2 is the indicator: ASA Capacity, Candor Gap, etc...
})

output$trade_popup <- renderUI({
  bsModal("modalTrade", paste0(Selected_Player()), "", size = "large",
          div(
            selectizeInput("tradeWhere", "Trade this player to:", choices = c("Retire","Adjust minutes","Replace with average player",teamDashboard$Tm), selected = NULL),
            actionButton("tradeButton", "Make this trade!"),
            textOutput("textTradeOutcome"),
            uiOutput('adjustMinutes'),
            uiOutput('tradedPlayers')
            )
  )
})

observeEvent(input$tradeButton, {

  values$showTradeText <- TRUE
  
  isolate({
    # if traded to a team, assign to targetTeam variable, else, target team is NULL. Same with players
    if (input$tradeWhere %in% teamDashboard$Tm) {
      targetTeam <- input$tradeWhere 
      targetPlayers <- input$tradedPlayers
    } else {
      targetTeam <- NULL
      targetPlayers <- NULL
    }
    # make the trade
    if (input$tradeWhere == "Adjust minutes") { # if only change in minutes of play
      values$playersAdjMin <- mutate(values$playersAdjMin, effMin = ifelse(Player == Selected_Player(), input$sliderMinutes/3936, effMin))
    } else { 
      if (input$tradeWhere=="Replace with average player") { # if actual trade
        averagePlayer$Tm <- filter(values$playersAdjMin, Player == Selected_Player())$Tm
        values$playersAdjMin <- bind_rows(values$playersAdjMin, averagePlayer)
      }
      values$playersAdjMin <- .trade_Players(data=values$playersAdjMin,playA=Selected_Player(),tmA=NULL, playB=targetPlayers, tmB=targetTeam) %>% arrange(Player)
    }
    
    # update players and teams resulting from trade
    playersPredictedStats_adjMin2 <- .redistributeMinutes(data = values$playersAdjMin, topHeavy = 7, topMinShare = .6, min_share_top1 = .105)
    playersPredictedStats_adjMin2 <- mutate(playersPredictedStats_adjMin2,Season = paste0(thisYear,"-",as.numeric(thisYear)+1)) %>% select(-Pick, -Exp) %>% as.data.frame()
    playersPredictedStats_adjPer <- group_by(playersPredictedStats_adjMin2, Tm) %>% mutate(effMin = effMin/sum(effMin,na.rm=TRUE)) %>% as.data.frame()

    #source("code_chunks/source_computeOffenseDefense.R",local=TRUE)
    # compute teams and players Offense and Defense
    playersNewPredicted_Final_adjMinPer2 <- select(playersPredictedStats_adjPer, -contains("Per"), -effFG, -effFGA, -effPTS, -effTRB)
    playersNewPredicted_OffDef <- mutate(playersNewPredicted_Final_adjMinPer2, Tm = Player, effMin = 1)
    playersPredicted <- .teamsPredictedPower(data = playersNewPredicted_OffDef,actualOrPred="predicted",maxs_vector = maxs_vector_input,
                                       mins_vector = mins_vector_input) %>%
      mutate(Player = substr(team_season,1,regexpr("_",team_season)-1),plusMinus = TEAM_PTS-TEAM_PTSAG) %>%
      select(Player,Offense = TEAM_PTS, Defense = TEAM_PTSAG, plusMinus) %>%
      as.data.frame()

    playersPredicted2 <- merge(playersPredicted,values$playersAdjMin[,c("Player","Exp","Age","Tm","effMin")], by ="Player") %>% mutate(adjPlusMinus = plusMinus*effMin*100) %>% group_by(Tm) %>% mutate(teamPlusMinus = sum(adjPlusMinus,na.rm=TRUE)) %>% ungroup()

    values$playersDatabase <- merge(playersPredictedStats_adjPer,select(playersPredicted2, -c(Age,Tm,effMin)), by = "Player")
    
    values$playersRanks <- mutate_if(values$playersDatabase, is.numeric, function(x) row_number(desc(x)))
    playerMax <- summarise_if(values$playersDatabase, is.numeric, max)
    playerMin <- group_by(values$playersDatabase, Player) %>% summarise_if(is.numeric, min)

    #source("code_chunks/source_predictedPowersWins.R",local=TRUE)
    teamsPredicted <- .teamsPredictedPower(data = playersNewPredicted_Final_adjMinPer2, actualOrPred="predicted",maxs_vector = maxs_vector_input,
                                       mins_vector = mins_vector_input)
    win_predictions <- .teamsPredictedWins(data = teamsPredicted) 

    values$teamsDatabase <- merge(teamsPredicted, win_predictions, by.x = "TeamCode", by.y = "team") %>%
      select(Tm = TeamCode, TeamOffense = TEAM_PTS, TeamDefense = TEAM_PTSAG, Season, wins)
    values$teamsRanks <- mutate_if(values$teamsDatabase, is.numeric, function(x) row_number(desc(x)))
    
    values$teamsStats <- .computeTeamStats(data = playersPredictedStats_adjPer)
    teamStatRanks <- mutate_if(values$teamsStats, is.numeric, function(x) row_number(desc(x)))
    values$teamsRanks <- merge(teamStatRanks, select(values$teamsRanks,-Season),by="Tm")
    values$teamsMax <- summarise_if(values$teamsStats, is.numeric, max)
    
    # update t_SNEs
    values$playersTSNE <- .compute_tSNE_ready_players(data = values$playersAdjMin) %>% as.data.frame()
    values$teamsTSNE <- .compute_tSNE_ready_teams(data = playersPredictedStats_adjPer) %>% as.data.frame()
    
    # A text informing of trade outcome
    output$textTradeOutcome <- renderText({
      if (values$showTradeText) {
        return(paste0(Selected_Player()," successfully traded to ",input$tradeWhere,". Please close this window to continue on the application"))
      } else {
        return()
      }
    })
    
    # update player dashboard selector
    updateSelectizeInput(session, "playerName", "Select Player", choices = select(values$playersDatabase,Player)$Player, selected = select(values$playersDatabase,Player)$Player[1])
    
  })

})

# observe adjust minutes of play
observeEvent(input$tradeWhere, {
  
  output$adjustMinutes <- renderUI({
    if (input$tradeWhere == "Adjust minutes") {
      #renderPrint(paste0("Est. minutes per game: ",round(filter(values$playersDatabase, Player == Selected_Player())$effMin*3936,1)))
      sliderInput('sliderMinutes',paste0('Current minutes: ',round(filter(values$playersAdjMin, Player == Selected_Player())$effMin*3936,1),'. Adjust minutes: '), min = 0, max = 48, value = round(filter(values$playersAdjMin, Player == Selected_Player())$effMin*3936,1))
    } else if (input$tradeWhere %in% teamDashboard$Tm) { # select players to trade for from target team
      checkboxGroupInput('tradedPlayers','Players to trade for:',choices = filter(values$playersAdjMin, Tm == input$tradeWhere)$Player,selected = NULL)
    } else return()
    
  })
  
})

```

### Create your own player
```{r}
fluidPage(
  fluidRow(
    column(4,textInput("create_name","Player name",width = '100%')),
    column(1,selectizeInput("create_position","Pos",choices = unique(playerDashboard$Pos),selected = NULL,width = '100%')),
    column(2,selectizeInput("create_team","Team",choices = unique(playerDashboard$Tm),selected = NULL,width = '80%')),
    column(1,selectizeInput("create_exp","Exp",choices = unique(playerDashboard$Exp),selected = "R",width = '100%')),
    column(2, sliderInput("create_age","Age",min = playerMin$Age, max = playerMax$Age,value = averagePlayer$Age)),
    column(2, sliderInput("create_min","Usage", min = 0, max = 48, value = round(mean(playersPredictedStats_adjMin$effMin)*3936,1)))
    #column(2, sliderInput("create_min","Usage",min = min(playersPredictedStats_adjMin$effMin), max = max(playersPredictedStats_adjMin$effMin),value = mean(playersPredictedStats_adjMin$effMin)))
  ),
  fluidRow(
    column(3, sliderInput("create_2PA","2 Point Attempt",min = playerMin$eff2PA, max = playerMax$eff2PA,value = averagePlayer$eff2PA,round = -2)),
    column(3, sliderInput("create_2PM","2 Point Made",min = playerMin$eff2PM, max = playerMax$eff2PM,value = averagePlayer$eff2PM,round = -2)),
    column(3, sliderInput("create_3PA","3 Point Attempt",min = playerMin$eff3PA, max = playerMax$eff3PA,value = averagePlayer$eff3PA,round = -2)),
    column(3, sliderInput("create_3PM","3 Point Made",min = playerMin$eff3PM, max = playerMax$eff3PM,value = averagePlayer$eff3PM,round = -2))
  ),
  fluidRow(
    column(3, sliderInput("create_FTA","FT Attempt",min = playerMin$effFTA, max = playerMax$effFTA,value = averagePlayer$effFTA,round = -2)),
    column(3, sliderInput("create_FTM","FT Made",min = playerMin$effFTM, max = playerMax$effFTM,value = averagePlayer$effFTM,round = -2)),
    column(3, sliderInput("create_ORB","Offensive Rebounds",min = playerMin$effORB, max = playerMax$effORB,value = averagePlayer$effORB,round = -2)),
    column(3, sliderInput("create_DRB","Defensive Rebounds",min = playerMin$effDRB, max = playerMax$effDRB,value = averagePlayer$effDRB,round = -2))
  ),
  fluidRow(
    column(2, sliderInput("create_AST","Assists",min = playerMin$effAST, max = playerMax$effAST,value = averagePlayer$effAST,round = -2)),
    column(2, sliderInput("create_BLK","Blocks",min = playerMin$effBLK, max = playerMax$effBLK,value = averagePlayer$effBLK,round = -2)),
    column(2, sliderInput("create_STL","Steals",min = playerMin$effSTL, max = playerMax$effSTL,value = averagePlayer$effSTL,round = -2)),
    column(3, sliderInput("create_TOV","Turnovers",min = playerMin$effTOV, max = playerMax$effTOV,value = averagePlayer$effTOV,round = -2)),
    column(3, sliderInput("create_PF","Personal Fouls",min = playerMin$effPF, max = playerMax$effPF,value = averagePlayer$effPF,round = -2))
  ),
  fluidRow(
    column(3, actionButton("createPlayerButton","Create Player")),
    column(9, dataTableOutput('newPlayer_stats'))
  )
)

observeEvent(input$createPlayerButton,{
  
  isolate({
    
     newPlayer <- data.frame(Player = as.character(input$create_name), Pos = as.character(input$create_position), Season = thisSeason, Age = input$create_age, Tm = as.character(input$create_team), Exp = as.character(input$create_exp), 
    FGPer= (input$create_2PM+input$create_3PM)/(input$create_2PA+input$create_3PA), FG3Per=input$create_3PM/input$create_3PA, FG2Per=input$create_2PM/input$create_2PA, effFGPer=(2*input$create_2PM+3*input$create_3PM)/(2*input$create_2PA+2*input$create_3PA),FTPer=input$create_FTM/input$create_FTA,
    effMin=input$create_min/3936,
    effFG=input$create_2PM+input$create_3PM,effFGA=input$create_2PA+input$create_3PA,eff3PM=input$create_3PM,eff3PA=input$create_3PA,eff2PM=input$create_2PM,eff2PA=input$create_2PA,effFTM=input$create_FTM,effFTA=input$create_FTA,effORB=input$create_ORB,effDRB=input$create_DRB,effTRB=input$create_ORB+input$create_DRB,effAST=input$create_AST,effSTL=input$create_STL,effBLK=input$create_BLK,effTOV=input$create_TOV,effPF=input$create_PF,effPTS=2*input$create_2PM+3*input$create_3PM+input$create_FTM,Pick=0, 
    stringsAsFactors = FALSE)
    
    values$playersAdjMin <- bind_rows(values$playersAdjMin, newPlayer)

    # update players and teams resulting from trade
    playersPredictedStats_adjMin2 <- .redistributeMinutes(data = values$playersAdjMin, topHeavy = 7, topMinShare = .6, min_share_top1 = .105)
    playersPredictedStats_adjMin2 <- mutate(playersPredictedStats_adjMin2,Season = paste0(thisYear,"-",as.numeric(thisYear)+1)) %>% select(-Pick, -Exp) %>% as.data.frame()
    playersPredictedStats_adjPer <- group_by(playersPredictedStats_adjMin2, Tm) %>% mutate(effMin = effMin/sum(effMin,na.rm=TRUE)) %>% as.data.frame()
    
    #source("code_chunks/source_computeOffenseDefense.R",local=TRUE)
    # compute teams and players Offense and Defense
playersNewPredicted_Final_adjMinPer2 <- select(playersPredictedStats_adjPer, -contains("Per"), -effFG, -effFGA, -effPTS, -effTRB)
playersNewPredicted_OffDef <- mutate(playersNewPredicted_Final_adjMinPer2, Tm = Player, effMin = 1)
playersPredicted <- .teamsPredictedPower(data = playersNewPredicted_OffDef,actualOrPred="predicted",maxs_vector = maxs_vector_input,
                                       mins_vector = mins_vector_input) %>%
  mutate(Player = substr(team_season,1,regexpr("_",team_season)-1),plusMinus = TEAM_PTS-TEAM_PTSAG) %>%
  select(Player,Offense = TEAM_PTS, Defense = TEAM_PTSAG, plusMinus) %>%
  as.data.frame()

    playersPredicted2 <- merge(playersPredicted,values$playersAdjMin[,c("Player","Exp","Age","Tm","effMin")], by ="Player") %>% mutate(adjPlusMinus = plusMinus*effMin*100) %>% group_by(Tm) %>% mutate(teamPlusMinus = sum(adjPlusMinus,na.rm=TRUE)) %>% ungroup()

    values$playersDatabase <- merge(playersPredictedStats_adjPer,select(playersPredicted2, -c(Age,Tm,effMin)), by = "Player")
    ### Here's where average player is lost
    values$playersRanks <- mutate_if(values$playersDatabase, is.numeric, function(x) row_number(desc(x)))
    playerMax <- summarise_if(values$playersDatabase, is.numeric, max)
    playerMin <- group_by(values$playersDatabase, Player) %>% summarise_if(is.numeric, min)

    #source("code_chunks/source_predictedPowersWins.R",local=TRUE)
    teamsPredicted <- .teamsPredictedPower(data =playersNewPredicted_Final_adjMinPer2, actualOrPred="predicted",maxs_vector = maxs_vector_input,
                                       mins_vector = mins_vector_input)
    win_predictions <- .teamsPredictedWins(data = teamsPredicted)

    values$teamsDatabase <- merge(teamsPredicted, win_predictions, by.x = "TeamCode", by.y = "team") %>%
      select(Tm = TeamCode, TeamOffense = TEAM_PTS, TeamDefense = TEAM_PTSAG, Season, wins)
    values$teamsRanks <- mutate_if(values$teamsDatabase, is.numeric, function(x) row_number(desc(x)))

    values$teamsStats <- .computeTeamStats(data = playersPredictedStats_adjPer)
    teamStatRanks <- mutate_if(values$teamsStats, is.numeric, function(x) row_number(desc(x)))
    values$teamsRanks <- merge(teamStatRanks, select(values$teamsRanks,-Season),by="Tm")
    values$teamsMax <- summarise_if(values$teamsStats, is.numeric, max)

    # update t_SNEs
    values$playersTSNE <- .compute_tSNE_ready_players(data = values$playersAdjMin) %>% as.data.frame(stringsAsFactors = FALSE)
    values$teamsTSNE <- .compute_tSNE_ready_teams(data = playersPredictedStats_adjPer) %>% as.data.frame(stringsAsFactors = FALSE)

    # update player dashboard selector
    updateSelectizeInput(session, "playerName", "Select Player", choices = select(values$playersDatabase,Player)$Player, selected = select(values$playersDatabase,Player)$Player[1])

  })
  
  output$newPlayer_stats <- renderDataTable({
    datatable(newPlayer,extensions = c('Scroller','FixedColumns'),
            options = list(dom='t',
                           pageLength = 1,
                           autoWidth = TRUE,
                           #deferRender = TRUE,
                           scrollY = 25,
                           scrollX = TRUE,
                           fixedColumns = list(leftColumns = 1),
                           scroller = TRUE,
                           initComplete = JS("function(settings, json) {","$(this.api().table().header()).css({'background-color': '#fff', 'color': '#575859', 'font-size': '10px', 'font-weight': 'bold'});","}")),
            rownames = FALSE) %>%
    formatRound(c('FGPer','FG3Per','FG2Per','effFGPer','FTPer','effMin'), 2) %>%
    formatStyle(0, target = 'row', fontSize = '70%', lineHeight = '70%')
  })

})

```

